% Auto-extracted from ../tfpt-42.tex for the TFPT 4.5 clean split.
% Source body assigned by the TFPT 4.5 clean split.

% ---- Original bibliography: source lines 14964-15051 ----
\begin{thebibliography}{99}

\bibitem{aps1975}
M.~F.~Atiyah, V.~K.~Patodi, and I.~M.~Singer,
\newblock \emph{Spectral asymmetry and Riemannian geometry. I},
\newblock Math. Proc. Cambridge Philos. Soc. \textbf{77} (1975), 43--69.

\bibitem{chamseddineConnes1997}
A.~H.~Chamseddine and A.~Connes,
\newblock \emph{The spectral action principle},
\newblock Commun. Math. Phys. \textbf{186} (1997), 731--750.

\bibitem{codata2022}
P.~J.~Mohr, D.~B.~Newell, and B.~N.~Taylor,
\newblock \emph{CODATA recommended values of the fundamental physical constants: 2022 update},
\newblock NIST / CODATA reference set, \url{https://physics.nist.gov/cuu/Constants/}, accessed March 2026.

\bibitem{pdg2025}
S.~Navas et al.\ (Particle Data Group),
\newblock \emph{Review of Particle Physics},
\newblock Phys.\ Rev.\ D \textbf{110} (2024), 030001; 2025 online update, \url{https://pdg.lbl.gov/2025/}, accessed March 2026.

\bibitem{nufit2025}
NuFIT Collaboration,
\newblock \emph{NuFIT global analysis of neutrino oscillation data},
\newblock website snapshot based on data available through November 2025, \url{https://www.nu-fit.org/}, accessed March 2026.

\bibitem{planck2018}
Planck Collaboration,
\newblock \emph{Planck 2018 results. VI. Cosmological parameters},
\newblock Astron. Astrophys. \textbf{641} (2020), A6.

\bibitem{LiddleLeach2003}
A.~R.~Liddle and S.~M.~Leach,
\newblock \emph{How long before the end of inflation was observable inflation?},
\newblock Phys. Rev. D \textbf{68} (2003), 103503; arXiv:astro-ph/0305263.

\bibitem{Bombieri1966}
E.~Bombieri,
\newblock \emph{On exponential sums in finite fields},
\newblock Amer. J. Math. \textbf{88} (1966), 71--105.

\bibitem{DeligneWeil}
P.~Deligne,
\newblock \emph{La conjecture de Weil. I},
\newblock Inst. Hautes \'Etudes Sci. Publ. Math. \textbf{43} (1974), 273--307.

\bibitem{PolyaVinogradov}
G.~P\'olya and I.~M.~Vinogradov,
\newblock completion-of-sums lemma; classical references include
G.~P\'olya, \emph{\"Uber die Verteilung der quadratischen Reste und Nichtreste},
Nachr. K\"on. Ges. Wiss. G\"ottingen (1918), 21--29, and
I.~M.~Vinogradov, \emph{Sur la distribution des r\'esidus et des non-r\'esidus des puissances},
J. Phys.-Math. Soc. Perm \textbf{1} (1918), 94--98; modern textbook treatment:
H.~Iwaniec and E.~Kowalski, \emph{Analytic Number Theory},
AMS Colloquium Publications \textbf{53} (2004), \S 12.4.

\bibitem{minamiKomatsu2020}
Y.~Minami and E.~Komatsu,
\newblock \emph{New extraction of the cosmic birefringence from the Planck 2018 polarization data},
\newblock Phys. Rev. Lett. \textbf{125} (2020), 221301.

\bibitem{eskilt2023}
J.~R.~Eskilt et al.,
\newblock \emph{Cosmoglobe DR1 results. II. Constraints on isotropic cosmic birefringence from reprocessed WMAP and Planck LFI data},
\newblock Astron. Astrophys. \textbf{679} (2023), A144.

\bibitem{sullivan2025}
R.~M.~Sullivan, A.~Abghari, P.~Diego-Palazuelos, L.~T.~Hergt, and D.~Scott,
\newblock \emph{Planck PR4 (NPIPE) map-space cosmic birefringence},
\newblock arXiv:2502.07654.

\bibitem{na62obs2025}
NA62 Collaboration,
\newblock \emph{Observation of the $K^{+}\to\pi^{+}\nu\bar{\nu}$ decay and measurement of its branching ratio},
\newblock JHEP \textbf{02} (2025), 191; arXiv:2412.12015.

\bibitem{na62Moriond2026}
X.~Chang et al.\ (for the NA62 Collaboration),
\newblock \emph{New measurement of $K^{+}\to\pi^{+}\nu\bar{\nu}$ branching ratio at the NA62 experiment},
\newblock arXiv:2604.12649; contribution to the 2026 Electroweak session of the 60th Rencontres de Moriond.

\bibitem{koto2024}
KOTO Collaboration,
\newblock \emph{Search for the $K_{L}\to\pi^{0}\nu\bar{\nu}$ decay at the J-PARC KOTO experiment},
\newblock arXiv:2411.11237.

\end{thebibliography}
