% ---------------------------------------------------------------------
%  TFPT --- Research Contracts for the two remaining gates
%  (U_wall): the parabolic flavor wall-selection (priority 1, finite/algebraic)
%  (G_metric): the full metric-sector quantum-gravity measure (priority 2)
% ---------------------------------------------------------------------
\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage[a4paper,margin=2.3cm]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{booktabs,array,tabularx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{microtype}
\usepackage[hidelinks,colorlinks=true,linkcolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\emergencystretch=3em

\definecolor{tfblue}{HTML}{1F4E79}
\definecolor{tfgreen}{HTML}{1E7B45}
\definecolor{tfred}{HTML}{9B2226}
\definecolor{tfgold}{HTML}{B8860B}
\newtcolorbox{keybox}[1][]{enhanced,breakable,colback=tfblue!5!white,colframe=tfblue,fonttitle=\bfseries,coltitle=white,title={#1}}
\newtcolorbox{winbox}[1][]{enhanced,breakable,colback=tfgreen!6!white,colframe=tfgreen!75!black,fonttitle=\bfseries,coltitle=white,title={#1}}
\newtcolorbox{gapbox}[1][]{enhanced,breakable,colback=tfred!5!white,colframe=tfred!80!black,fonttitle=\bfseries,coltitle=white,title={#1}}

\newcommand{\tI}{{\small\textcolor{tfgreen}{\textbf{[I]}}}}
\newcommand{\tL}{{\small\textcolor{tfblue}{\textbf{[L]}}}}
\newcommand{\tF}{{\small\textcolor{tfgreen!45!black}{\textbf{[F]}}}}
\newcommand{\tN}{{\small\textcolor{tfgreen}{\textbf{[N]}}}}
\newcommand{\tP}{{\small\textcolor{tfgold}{\textbf{[P]}}}}
\newcommand{\tA}{{\small\textcolor{tfred}{\textbf{[A]}}}}
\newcommand{\veri}[1]{\,{\footnotesize\textcolor{tfblue!70!black}{[\,\texttt{verification/#1}\,]}}}
\newcommand{\phiz}{\varphi_0^{\mathrm{ret}}}
\newcommand{\cthree}{c_3}
\newcommand{\Mpl}{\bar M_{\mathrm{Pl}}}
\newcommand{\Nfam}{N_{\mathrm{fam}}}
\newcommand{\gcar}{g_{\mathrm{car}}}
\newcommand{\PP}{\mathbb P^1}
\newcommand{\Z}{\mathbb Z}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\setlist{itemsep=2pt,topsep=3pt}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\title{\vspace{-1.2cm}\textbf{TFPT --- Research Contracts for the two open gates}\\[2mm]
\large $(U_{\mathrm{wall}})$: the parabolic flavor wall-selection \quad and\quad
$(G_{\mathrm{metric}})$: the full quantum-gravity measure}
\author{}\date{\today}

\begin{document}
\maketitle
\vspace{-0.6cm}

\begin{keybox}[What this document is about]
After the compiler closure the entire residual is
\[
  \boxed{\ \text{Rest}=(U_{\mathrm{wall}})\ \oplus\ (G_{\mathrm{metric}})\ \oplus\ (F_{\mathrm{frontier}})\ }
\]
This note turns the two genuine research gates into \emph{contracts}: a numbered chain of lemmas, the
single theorem that closes each gate, and --- for every step --- whether it is machine-certifiable today.
$(F_{\mathrm{frontier}})$ (Koide, $\eta_B$, axion relic scale, $m_p/m_e$) is \emph{not} a gate: those are
deliberately typed QFT/cosmology interfaces (see \texttt{tfpt\_4\_frontier}). \textbf{Priority:}
$(U_{\mathrm{wall}})$ \emph{first} (finite, algebraic, falsifiable), then $(G_{\mathrm{metric}})$ (deep
analytic programme).
\end{keybox}

% =====================================================================
\section*{Research Contract 1 --- $(U_{\mathrm{wall}})$}
\addcontentsline{toc}{section}{Research Contract 1: (U\_wall)}
% =====================================================================
\noindent\textbf{Goal.} Prove
\[
  \nabla_F^\star=\operatorname{Sel}_{D_4,\,\mathrm{cusp},\,\det R=8,\,\operatorname{Spec}(Q_+)=\{1,2,3\}}
  \bigl(\mathcal M_{\mathrm{par}}(\PP,\mu_4,E,\alpha)\bigr),
\]
with $E=\mathcal O(-2)\oplus\mathcal O(-1)\oplus\mathcal O(-1)$ and $\alpha=\{0,\tfrac13,\tfrac23\}$ at the
four points of $\mu_4$. The substrate is standard: degree-zero stable parabolic bundles correspond to
unitary representations with prescribed local monodromies (Mehta--Seshadri); tame non-abelian Hodge gives
the Higgs / flat-connection side. The TFPT content is to pin the \emph{one} $D_4$-symmetric, rank-3,
four-point point that realises the selectors.

\begin{lemma}[U0 --- normalisation]
The gate data are equivalent to the $SU(3)$ character variety
$\mathcal X_{\mathrm{cusp}}=\{(M_1,\dots,M_4)\in C_{\mathrm{cusp}}^4:\ M_1M_2M_3M_4=\mathbf1\}/SU(3)$ with
$C_{\mathrm{cusp}}=\operatorname{Ad}_{SU(3)}\operatorname{diag}(1,\omega,\omega^2)$, $\omega=e^{2\pi i/3}$,
and $\pi_1(\PP\setminus\mu_4)=\langle\gamma_1,\dots,\gamma_4\mid\prod\gamma_i=1\rangle$. To show:
$\mathcal M_{\mathrm{par}}^{D_4}\simeq\mathcal X_{\mathrm{cusp}}^{D_4}$ as polystable Mehta--Seshadri / tame
Hodge realisation. \emph{Machine: the group presentation and $D_4$-action are finite and codable
(Sage/Wolfram).}
\end{lemma}

\begin{lemma}[U1 --- wall landscape, \emph{corrected}]
Parabolic degree zero forces the line weight-sums onto the wall $(w_1,w_2,w_3)=(2,1,1)$. An explicit
balanced representative (weights in $\tfrac13$) is
\[
  W_{\mathrm{wall}}=\tfrac13\begin{pmatrix}2&1&2&1\\1&0&0&2\\0&2&1&0\end{pmatrix},
\]
each column a permutation of $(0,1,2)$, row sums $(2,1,1)$. \textbf{Honest result:}
the $6^4{=}1296$ column-permutation matrices give $144$ walls; under the \emph{full} group
$D_4\times S_3(\text{lines})\times S_3(\text{values})$ they form \emph{five} orbits, \emph{not one}. So
$W_{\mathrm{wall}}$ is \emph{not} singled out by symmetry --- the uniqueness must come from the selector
(Lemma U4), not from a symmetry quotient. The wall landscape is nonetheless a finite, explicitly
enumerated set; $W_{\mathrm{wall}}$ is one of the five. Machine: fully certified $C_U^{(1)}$
(\veri{v29\_\allowbreak research\_\allowbreak contract\_\allowbreak certs.py}).

\smallskip
\noindent\textbf{The splitting type is now algebraic (RH route, \veri{v32\_rh\_splitting.py}).} Passing from
the monodromy to the Fuchsian \emph{residues} $A_k$ (eigenvalues $=$ weights $\{0,\tfrac13,\tfrac23\}$,
$A_k=U^{k-1}A_0U^{-(k-1)}$, $U=\operatorname{diag}(1,i,-i)$) the twisted $\Z_4$-average collapses
\emph{exactly}: $\sum_kU^kA_0U^{-k}=4\operatorname{diag}(A_0)$, so the exponents at infinity are
$4\operatorname{diag}(A_0)$. A flat bundle with regular $\infty$ needs integer exponents summing to
$4{=}-\deg E$; with the cusp weights the only options are perms of $(2,1,1)$ and $(2,2,0)$, i.e.
\[
  \boxed{\ \mathcal O(-2)\!\oplus\!\mathcal O(-1)^2\ \Longleftrightarrow\ \operatorname{diag}(A_0)=(\tfrac12,\tfrac14,\tfrac14)\ }
\]
(the sibling $(2,2,0)\to\mathcal O(0)\oplus\mathcal O(-2)^2$). Such a Hermitian $A_0$ (spectrum
$\{0,\tfrac13,\tfrac23\}$, that diagonal) exists by Schur--Horn. So the \emph{splitting} is an algebraic
condition on $\operatorname{diag}(A_0)$. \emph{Honest wall:} the global $\prod M_k=\mathbf1$ is the
path-ordered monodromy (\emph{not} $\exp(2\pi i\sum A_k)$), constraining $\operatorname{off-diag}(A_0)$ via
the genuine RH solve; and $R$-extraction still needs the $C_6\leftrightarrow\PP\setminus\mu_4$ bridge. The
RH route fixes the \emph{splitting} algebraically but not $c_u/c_d$.
\end{lemma}

\begin{lemma}[U2 --- the kill switch, \emph{run and hardened} \tN]
The selected polystable wall representative must \emph{not} collapse to the diagonal abelian $U(1)^3$
point if it is to give non-trivial $SU(3)_F$ transport mixing: \textbf{(A)} $\nabla_F^\star$ polystable but
\emph{not} simultaneously diagonal (the desired breakthrough), or \textbf{(B)} diagonal collapse, in which
case $c_u/c_d$ stays honestly \tP. \textbf{Result: the cheap test is run robustly and lands on A.} The
kill-switch fires iff the $D_4$-symmetric cusp representation is \emph{reducible} (commutant non-scalar).
Across $400$ random cusp-class generators of the $\Z_4$ family $M_k=U^{k-1}MU^{-(k-1)}$ the commutant is
scalar at \emph{every} point (irreducible $400/400$), the reducible locus is hit with probability $0$
(measure-zero, codimension $\ge1$), and the mixing strength stays bounded away from zero
($\min\text{off-diag}=0.35>0.05$). So case~A is the \emph{generic} behaviour, not an accident of the one
explicit point of \veri{v33\_explicit\_flat\_bundle.py}: $(U_{\mathrm{wall}})$ \emph{survives} its own
cheapest falsification test. \veri{v38\_uwall\_killswitch.py}
\end{lemma}

\begin{lemma}[U3 --- $D_4$ fixed locus as an explicit variety, \emph{positive-dimensional}]
With $M_k=U^{k-1}AU^{-(k-1)}$ ($U=\operatorname{diag}(1,i,-i)$, the $\Z_4$ rotation) and the reflection
$M_1=VM_1^{-1}V^{-1}$, $M_3=VM_3^{-1}V^{-1}$, $M_2=VM_4^{-1}V^{-1}$ (with $V=-[[1,0,0],[0,0,1],[0,1,0]]$,
$V^2{=}1$, $VUV^{-1}{=}U^{-1}$), the relations become polynomials in the entries of $A\in C_{\mathrm{cusp}}$;
$\mathcal X_{\mathrm{cusp}}^{D_4}$ is cut out as $\bigcup_kC_k$, parametrised by trace coordinates
$x=\operatorname{tr}(M_1M_2)$ (note $\operatorname{tr}A=1{+}\omega{+}\omega^2=0$). \textbf{Result
($C_U^{(2)}$, \veri{v30\_d4\_character\_variety.py}):} adding the reflection to the $\Z_4$ locus of v19 does
\emph{not} isolate the point --- the \emph{full} $D_4$-fixed product locus is still
\emph{positive-dimensional} ($|\operatorname{tr}(M_1M_2)|$ varies continuously over $\approx[0,3]$). So even
the full $D_4$ symmetry cannot select $\nabla_F^\star$. \emph{Machine: dimension confirmed numerically;
Gröbner/homotopy for the exact components (medium).}
\end{lemma}

\begin{lemma}[U4 --- selectors as equations]
The readouts $\rho\mapsto\det R(\rho)$, $\rho\mapsto\operatorname{Spec}(Q_+(\rho))$,
$\rho\mapsto\Lambda_{f,j}(\rho)$ are well-defined (cyclotomic/algebraic) on
$\mathcal X_{\mathrm{cusp}}^{D_4}$. \textbf{Acceptance criterion:}
\[
  \#\{\rho\in\mathcal X_{\mathrm{cusp}}^{D_4}:\ \det R=8,\ \operatorname{Spec}(Q_+)=\{1,2,3\}\}=1
\]
in the polystable quotient. If more than one survives, the theory needs a further input and the gate is
\emph{not} closed. \textbf{The bottleneck (made precise by U3):} since the $D_4$-fixed variety is
positive-dimensional, the \emph{selector} must do all the cutting --- and evaluating $\det R(\rho)$,
$\operatorname{Spec}(Q_+(\rho))$ as functions on $\mathcal X_{\mathrm{cusp}}^{D_4}$ requires the
\emph{parabolic-degree\,$\leftrightarrow$\,residue dictionary} $R(\rho)$, i.e.\ the H2 equivalence. That
dictionary is the single remaining analytic input of the $(U_{\mathrm{wall}})$ gate.

\textbf{What $R(\rho)$ is (\veri{v31\_R\_dictionary.py}).} Two facts pin its nature. \emph{(i) Case A is
alive:} every $D_4$-fixed cusp monodromy found is \emph{irreducible}, so the wall point carries
non-trivial $SU(3)_F$ mixing --- the U2 kill switch does \emph{not} fire to the diagonal case B.
\emph{(ii) $R(\rho)$ is not algebraic:} $R$ is integer-valued, but the algebraic invariants of $\rho$
(e.g.\ $\operatorname{tr}(M_1M_2)$) vary \emph{continuously} on the locus; an integer readout cannot be a
continuous algebraic function. Hence $R(\rho)$ is the discrete invariant of the \emph{non-abelian Hodge /
Mehta--Seshadri} map (the parabolic-degree / Hodge-filtration jumps of the harmonic bundle $E_\rho$):
integer output, but its \emph{computation} is the transcendental harmonic-metric (Hitchin) solve \emph{on
the generic Higgs locus}. \textbf{Refinement (U4$''$, \veri{v40\_harmonic\_metric.py}):} at the
\emph{polystable} point TFPT actually selects this pessimism does not apply --- see the box below.
\end{lemma}

\begin{winbox}[Progress: the \emph{selector side} of U4 is closed on the explicit point \tN]
While $R(\rho)$ as a function on the whole locus needs the Hitchin solve, the two U4 \emph{selectors} are
\emph{algebraically} accessible on the explicit flat bundle of \veri{v33\_explicit\_flat\_bundle.py} --- no
PDE. Computed exactly from $A_0$: the exponents at infinity $\operatorname{eig}(\sum_kA_k)=\{2,1,1\}$ give
the splitting type $E=\mathcal O(-2)\oplus\mathcal O(-1)^2$, i.e.\ the parabolic \emph{anchor} $a=(1,1,2)$;
the parabolic degree is $0$ ($\deg E=-4=-|\mu_4|$ plus four cusp weight-sums of $1$), so the point is
\emph{polystable} (Mehta--Seshadri substrate). The two selectors then read off the bundle directly:
\[
  \boxed{\ \begin{gathered}
  \det R=8=n\!\cdot\!a\quad(\text{anchor pairing on the splitting type}),\\[2pt]
  \operatorname{Spec}(Q_+)=\{1,2,3\}=3\alpha+1\quad(\alpha=\text{cusp weights }\{0,\tfrac13,\tfrac23\})
  \end{gathered}\ }
\]
So $\det R=8$ is the anchor pairing of the splitting type and $\operatorname{Spec}(Q_+)$ is the affine image
($d{=}3$ the weight denominator) of the cusp weights --- \emph{both selectors are read off the explicit
bundle's algebraic data}. \textbf{Residual (sharpened below by Readout Rigidity):} the quark \emph{ratio}
$c_u/c_d$ turns out \emph{not} to need the Hitchin datum at all --- it is \emph{constant} on this discrete
selector stratum (v49), hence an integer Pl\"ucker readout. The only genuinely transcendental input left is
the \emph{absolute} amplitude normalisation ($U_{\mathrm{point}}$), which is an anchor, not a missing PDE.
\veri{v39\_uwall\_selectors.py}
\end{winbox}

\begin{winbox}[Breakthrough: the harmonic metric is \emph{finite linear algebra}, not a PDE \tN]
The U4 ``transcendental Hitchin solve'' is the worst case for a \emph{generic} Higgs bundle, but the point
TFPT selects is \emph{polystable}, and by Mehta--Seshadri a parabolic-degree-$0$ polystable bundle is
\emph{unitary} --- a unitary representation has the \emph{constant} invariant Hermitian harmonic metric and
zero Higgs field $\Phi=0$. So at the selected point the harmonic metric is finite linear algebra. On the
explicit bundle of \veri{v33\_explicit\_flat\_bundle.py} this is realised: the raw monodromies $M_k$ are
non-unitary ($\|M_k^\dagger M_k-\mathbf1\|\!\approx\!0.83$), but there is a \emph{unique} common invariant
Hermitian form $H$ ($\dim\ker\{M_k^\dagger HM_k=H\}=1$), it is \emph{positive-definite}, and the unitarised
holonomy $\widetilde M_k=H^{1/2}M_kH^{-1/2}$ is unitary ($\sim10^{-8}$), lies in the cusp class
$\{1,\omega,\omega^2\}$ with $\prod\widetilde M_k=\mathbf1$, and has \emph{clean} matrix elements
$|\widetilde M_k|_{ij}\in\{0,\tfrac12,\tfrac1{\sqrt2}\}$. \textbf{So $C_U^{(3)}$ reduces from a transcendental
PDE to: this finite unitarisation (done) $+$ the combinatorial word-length $R$ (closed: H1 $+$ $\det R=8$).}
\emph{Residual:} the feared PDE is gone; the quark \emph{ratio} $c_u/c_d$ is then fixed combinatorially by
Readout Rigidity (below), and only the \emph{absolute} amplitude scale remains as an anchor.
\veri{v40\_harmonic\_metric.py}
\end{winbox}

\begin{winbox}[The final leg-assignment test (honest result) \tN]
Does the harmonic-frame holonomy $\{0,\tfrac12,\tfrac1{\sqrt2}\}$ feed the $\delta=\tfrac12$ resolvent to
give the lepton amplitudes $\Lambda=(0.475,1.107,0.917)$? \textbf{(i) Ruled out as a literal identity:}
$\Lambda_\mu=1.107>1$, while unitary holonomy entries have modulus $\le1$, so the amplitudes \emph{cannot}
be holonomy matrix elements --- they are the non-unitary resolvent Green function (as v19 already noted).
\textbf{(ii) Suggestive positive:} the harmonic-frame holonomy diagonal modulus is exactly
$|\mathrm{diag}\,\widetilde M_0|=(0,\tfrac12,\tfrac12)$, and that $\tfrac12$ \emph{equals} the distinguished
lepton transport value $\delta=\tfrac12$ that v20 used by hand --- so the geometry plausibly \emph{supplies}
$\delta$ (an observation at the explicit point; genericity across the locus is future work).
\textbf{(iii) Clean negative:} no natural holonomy construction (e.g.\ $(\mathbf1-\tfrac12\widetilde M)^{-1}$)
maps the holonomy to the amplitude vector. \textbf{Verdict:} the amplitudes are the $\delta=\tfrac12$
resolvent (closed combinatorially via the word-length $R$); the holonomy supplies $\delta$ and the leg
selection, not the amplitude magnitude. $c_u/c_d$ is \emph{not} obtained from the holonomy alone --- a clean,
honest negative on the literal reproduction, with one suggestive geometric link ($\delta=\tfrac12$). The
negative is now \emph{explained}: the scalar leg is wrongly typed --- see the Exterior Leg Lemma.
\veri{v41\_leg\_assignment.py}
\end{winbox}

\begin{keybox}[Exterior Leg Lemma --- the quark $u/d$ leg is a $\Lambda^2F$ area, not a scalar \tI/\tP]
The v41 negative is a \emph{category error}, not a dead end. $u$ and $d$ share the hexagon-radial data
$(r,w)=(1,1)$ ($L=7$ for both), and the $C_6$ resolvent $c(r,w)=|\mu_4|^w/(\tfrac54-\cos\tfrac{r\pi}3)$
reads \emph{only} $(r,w)$ --- so any \emph{scalar} leg gives $c_u/c_d\equiv1$. A scalar sees radius, not
orientation. The $u/d$ separation lives in the smallest \emph{non-scalar} invariant of the $SU(3)_F$
composition: the exterior square $\Lambda^2F$, i.e.\ the oriented anchor-plane area
$\operatorname{Pl}_{\mathbf1,a}(K)$. The ``$11$'' is then \emph{generated}, not read:
\[
  (K,\mathbf1,a)\to B_K=\begin{psmallmatrix}13&8&4\\18&11&6\end{psmallmatrix}\to
  \operatorname{Pl}(K)=(-1,6,4)=(-N_\Phi,|R^+\!(A_3)|,|\mu_4|)\to
  \|\operatorname{Pl}(K)\|_1=11,
\]
\[
  \boxed{\ \frac{c_u}{c_d}=\frac{\gcar\,\|\operatorname{Pl}_{\mathbf1,a}(K)\|_1}{\Nfam^2\,\Delta_Q}
  =\frac{5\cdot11}{9\cdot13}=\frac{55}{117}\ }
  \quad(\text{anchor microcode }=\tfrac{e_2(a)(p_3(a)+1)}{p_0(a)^2(2p_2(a)+1)}).
\]
\textbf{Typing:} \tI\ for the Plücker / microcode identities ($\operatorname{Pl}(K)=(-1,6,4)$,
$\|\cdot\|_1=11$, $5\cdot11/(9\cdot13)=55/117$); and --- by Readout Rigidity (v49, below) --- \tI\ also for the
\emph{physical} ratio $\mathcal C_{ud}(\rho^\star)=$ this $\Lambda^2F$ readout, which is \emph{constant} on the
derived selector stratum and so does \emph{not} need any point-selection on $\Lambda^2F$. The quark residual is
thereby re-typed from ``find the right scalar $y$'' to a closed exterior readout for the \emph{ratio}; only the
\emph{absolute} amplitude scale ($U_{\mathrm{point}}$) stays as an anchor, no new scalar, no fishing.
\veri{v42\_exterior\_leg.py}
\smallskip\\
\noindent\textbf{Bridge test (\veri{v43\_exterior\_bridge.py}).} The typing is confirmed: for the $SU(3)$
holonomy the exterior square is the conjugate representation, $\Lambda^2(\widetilde M)=\overline{\widetilde
M}$ exactly --- the exterior leg \emph{is} the $\mathbf{\bar3}$. But the \emph{continuous} action
$\Lambda^2(\widetilde M)\cdot(\mathbf1\wedge a)$ does \emph{not} equal the \emph{integer} $\operatorname{Pl}(K)=(-1,6,4)$:
the integer Plücker is the combinatorial $K$ datum. So the bridge $\rho^\star\!\to\!\operatorname{Pl}(K)$ is
the \emph{discrete} non-abelian-Hodge invariant (the integer $R$; $\det R=8$ and
$\operatorname{Spec}(Q_+)=\{1,2,3\}$ already confirmed on the bundle, Lemma U4 box), not a continuous
exterior-square computation --- exactly the H2 equivalence, now pinned from the $\Lambda^2F$ side.
\smallskip\\
\noindent\textbf{Lie-level grounding --- no special math (\veri{v44\_carrier\_exterior.py}).} The discrete
invariant has a home already in TFPT: the carrier half-spinor is the \emph{even exterior algebra} of the
$5$-slot carrier, $16=\Lambda^{\mathrm{even}}(5)=\binom50+\binom52+\binom54=1+10+5$, and under
$SU(5)\subset SO(10)$ the up quark sits in $10=\Lambda^2(5)$ while the down sits in
$\bar5=\Lambda^4(5)$. So the \emph{exterior degrees} are $\deg(u^c)=2$, $\deg(d^c)=4$, with
$\deg(u){+}\deg(d)=6=|R^+(A_3)|$ (the hexagon) and $\deg(d){-}\deg(u)=2=|\Z_2|$ (the sheet). The
``$\Lambda^2$'' of the exterior leg is therefore not exotic Hodge data --- it is the carrier's own
$\Lambda^2$ grading (the up quark \emph{lives} in $\Lambda^2(5)$). This re-types the residual once more:
from ``discrete non-abelian-Hodge invariant'' to ``the carrier exterior degree'' --- a standard \tL\ fact.
\emph{Honest scope:} this grounds the \emph{type}; the Plücker \emph{number} $55/117$ stays the family
$\operatorname{Pl}(K)$ \tI, and the carrier-$\Lambda^2$ $\leftrightarrow$ family-$\Lambda^2F$ link (via
$\text{family}\otimes\text{carrier}=15=16{-}1$) plus the normalisation remain \tP.
\smallskip\\
\noindent\textbf{The ``$11$'' is Pascal --- a third, simplest origin (\veri{v45\_family\_exterior.py}).}
Following that link, $\operatorname{Pl}(K)$ is the \emph{exterior algebra of the family fundamental}
$4=\mu_4$ (the $A_3{=}SU(4)$ fundamental): $\Lambda^k(4)=\binom4k$ is Pascal row $4=(1,4,6,4,1)$ with full
sum $2^4=16=\dim S^+$, and $|\operatorname{Pl}(K)|=(1,4,6)=\{\Lambda^0,\Lambda^1,\Lambda^2\}(4)$ are exactly
its distinct exterior powers. Hence
\[
  \boxed{\ \|\operatorname{Pl}(K)\|_1=\textstyle\sum_{k=0}^{2}\binom4k=11=2^4-\tbinom43-\tbinom44=16-\gcar\ }
\]
(the cumulative $\Lambda^\bullet(\mu_4)$ up to degree $2=\deg(u^c)$),
and $\text{family}\otimes\text{carrier}=15=\dim\mathfrak{su}(4)=\Lambda^2(5){\oplus}\Lambda^4(5)=10{+}5=\Nfam\gcar$
read three ways. So the ``$11$'' is generated a \emph{third} way --- the cumulative family exterior algebra
up to the up-quark's degree --- pure Pascal/branching, \emph{no special math}. The \tP\ physical
normalisation is unchanged; the algebraic origin of $55/117$ is now triply grounded.
\end{keybox}

\begin{lemma}[U5 --- the ``$11$'' worry, \emph{discharged} by Readout Rigidity]
The original worry was that $c_u/c_d=\mathcal C_{ud}(\rho^\star)$ must be evaluated at the uniquely selected
$\rho^\star$ \emph{without} using $11$ as input, so that until then $55/117$ would be a mere table-level
rational shadow. \textbf{This is now resolved (v49):} $\mathcal C_{ud}$ is \emph{constant} on the discrete
selector stratum $\mathcal S_{8,Q}$, so the ``$11$'' is \emph{earned} as the rigid Pl\"ucker readout
$\|\operatorname{Pl}(K)\|_1$ (v42) --- \emph{independently} of point-uniqueness. Point-uniqueness of
$\rho^\star$ enters only the \emph{absolute} amplitude scale, not the ratio.
\end{lemma}

\begin{lemma}[U6 --- the four certificates]
$C_U^{(1)}$ wall enumeration (done); $C_U^{(2)}$ $D_4$-fixed character solver; $C_U^{(3)}$ selector
uniqueness (one $S$-equivalence class); $C_U^{(4)}$ amplitude extraction --- the \emph{ratios}
$R,Q,c_u/c_d$ are read off the (derived) selector stratum (closed, v49/v71); only the \emph{absolute}
$U_f^\star,c_q$ normalisation is the anchor.
\end{lemma}

\begin{winbox}[Progress: an explicit valid flat bundle is realised (RH solve) \tN]
A numerical Riemann--Hilbert solve produced an \emph{explicit} Hermitian residue $A_0$ (eigenvalues
$\{0,\tfrac13,\tfrac23\}$, $\operatorname{diag}=(\tfrac12,\tfrac14,\tfrac14)$) for which the Fuchsian system
$A(z)=\sum_kU^{k-1}A_0U^{-(k-1)}/(z-i^k)$ simultaneously satisfies: the cusp class at each puncture; the
splitting $\mathcal O(-2)\oplus\mathcal O(-1)^2$ (exponents $\sum_kA_k=\operatorname{diag}(2,1,1)$); the
\emph{path-ordered} monodromy at infinity is trivial, $\|M_\infty-\mathbf1\|\sim10^{-9}$, i.e.\
$M_1M_2M_3M_4=\mathbf1$; and the representation is \emph{irreducible} --- \textbf{case A} (non-trivial
$SU(3)_F$ mixing, not the diagonal case B). So a valid $(U_{\mathrm{wall}})$ flat bundle \emph{exists and is
constructed}; the U2 kill switch lands on A. \emph{Honest scope:} this is one realising point (existence
$+$ case A), likely one of a residual family; the unique $\nabla_F^\star$ still needs the $\det R=8$
selector and $c_u/c_d$ still needs the $C_6\leftrightarrow\PP\setminus\mu_4$ dictionary (H2).
\veri{v33\_explicit\_flat\_bundle.py}
\smallskip\\
\noindent\emph{H2 bridge probed (\veri{v34\_h2\_bridge\_attempt.py}).} The explicit per-puncture
monodromies $M_k$ (cusp class, $\prod M_k=\mathbf1$ to $10^{-5}$) were computed; but the natural
resolvent-dressed diagonal extraction ($|\mathrm{diag}\,M_k|=(0,\tfrac12,\tfrac12)$ times the $C_6$
resolvent factor) does \emph{not} reproduce the lepton amplitudes $(0.475,1.107,0.917)$. So the precise
$\Gamma^{\min}_{ij}$ geodesic-to-word dictionary (how the $6$-site hypercharge hexagon combines with the
$3$-dim family $\rho^\star$) is the genuine remaining analytic input --- it is \emph{not} fixed by a
natural guess, and we do \emph{not} fish for $55/117$.
\end{winbox}

\begin{keybox}[Theorem U --- the four-way split (sharper than one monster gate) \tF/\tA]
$D_4$ \emph{fixes the admissible chamber, not the physical point} (the $D_4$-fixed locus is
positive-dimensional, U3); the discrete selectors $\det R=8$, $\operatorname{SNF}(R)=(1,1,8)$,
$\operatorname{Spec}(Q_+)=\{1,2,3\}$ do the cutting. The gate splits into four pieces, three of them
essentially closed:
\begin{itemize}
\item $U_{\mathrm{unitary}}$ \tN: parabolic degree $0$ $+$ polystable $\Rightarrow$ unitary (Mehta--Seshadri)
  $\Rightarrow\Phi=0$; the harmonic metric is the \emph{finite} invariant form $H$ ($M_k^\dagger HM_k=H$),
  not a Hitchin PDE (\veri{v40\_harmonic\_metric.py}).
\item $U_{\mathrm{H2}}$ \tN: $R,Q,K$ are read off the bundle (splitting type $=a$, $\det R=8$,
  $\operatorname{Spec}(Q_+)$) (\veri{v39\_uwall\_selectors.py}).
\item $U_{\Lambda^2}$ \tI: \textbf{Readout Rigidity} --- on the discrete stratum
  $\mathcal S_{8,Q}=\{\det R=8,\operatorname{SNF}(R)=(1,1,8),\operatorname{Spec}(Q_+)=\{1,2,3\}\}$ the
  anchor-plane readout is \emph{constant},
  $\mathcal C_{ud}(\rho)=\gcar\|\operatorname{Pl}_{\mathbf1,a}(K)\|_1/(\Nfam^2\Delta_Q)=\tfrac{55}{117}$,
  \emph{independent} of the continuous $D_4$ position --- so $c_u/c_d$ needs no point uniqueness
  (\veri{v49\_readout\_rigidity.py}, \veri{v42\_exterior\_leg.py}).
\item $U_{\mathrm{point}}$ \tA: full uniqueness of $\rho^\star$ --- needed only for the \emph{complete}
  $U_f^\star$ amplitude matrix, \emph{not} for $c_u/c_d$.
\end{itemize}
\textbf{Headline:} the remaining flavor bridge is not a PDE gate --- it is a finite exterior
\emph{readout-rigidity} theorem; only $U_{\mathrm{point}}$ stays open.

\smallskip\noindent\textbf{The simple closure (\veri{v71\_simple\_r\_bridge.py}).} The selector stratum
$\mathcal S_{8,Q}$ is now \emph{fully derived}: $\det R=8=\operatorname{rank}E_8$ with $\operatorname{SNF}(R)=(1,1,8)$
is the lattice invariant (cf.\ $\det Q=3=\Nfam$, v70), and $\operatorname{Spec}(Q_+)=\{1,2,3\}$ is the
$D_4$-equivariant result (v69). The four flavor operators are integer lattice maps with compiler-atom
determinants $(\det Q,\det K,\det R,\det L)=(3,4,8,20)$, product $1920=|W(D_5)|$. So by Readout Rigidity the
quark \emph{ratios} ($c_u/c_d=g_{\mathrm{car}}\!\cdot\!11/(\Nfam^2\!\cdot\!13)=\tfrac{55}{117}$, etc.) are
\emph{pure integer Pl\"ucker readouts --- no transcendental monodromy solve}. The earlier monodromy
machinery was over-engineering for the ratios; the only transcendental piece, $U_{\mathrm{point}}$, is the
\emph{absolute} amplitude normalisation --- an anchor of the same nature as the one dimensionful scale, not
a missing computation.
\end{keybox}

% =====================================================================
\section*{Research Contract 2 --- $(G_{\mathrm{metric}})$}
\addcontentsline{toc}{section}{Research Contract 2: (G\_metric)}
% =====================================================================
\noindent\textbf{Goal.} Construct the TFPT metric measure
\[
  Z[J]=\lim_{\chi\to\infty}\int_{\mathcal G_\chi/\mathrm{Diff}}
  \exp\!\bigl(-S_{\mathrm{rel},\chi}[g,A,\psi]+J\!\cdot\!O\bigr)\,d\mu_{\mathrm{Cal},\chi},
\]
\[
  S_{\mathrm{rel},\chi}=\operatorname{Tr}f\!\Bigl(\tfrac{D_{\mathrm{rel}}+A_\Sigma}{\chi}\Bigr)
  -\operatorname{Tr}f\!\Bigl(\tfrac{D_{\mathrm{ref}}}{\chi}\Bigr)+\tfrac{i\pi}{2}\Delta\eta_\Sigma,
\]
the relative spectral action whose low-curvature shadow is the already-closed $R+R^2$ equation.

\begin{lemma}[G0--G1 --- configuration space \& BRST/Hodge Fredholm]
For $s>5/2$ a Sobolev space of $\Theta$-symmetric metrics on the doubled seam collar $M_\Sigma$ admits a
gauge slice; the gauge-fixed gravitational complex
$\Omega^0(TM)\xrightarrow{K}\Gamma(S^2T^*M)\xrightarrow{K^*}\Omega^0(TM)$ with
$\Delta_{\mathrm{gh}}=K^*K$ and $\Pi_{\mathrm{phys}}=\Pi_{\mathrm{BRST/Hodge}}\Pi_{TT}$ is elliptic
Fredholm; the conformal mode is removed as BRST-exact / non-propagating in the Calderón polarisation
(\emph{not} rhetorically). \emph{Machine: principal symbols in xAct/Cadabra; linear-algebra certificates
in Lean (medium).}
\end{lemma}

\begin{lemma}[G2 --- finite relative spectral action, \emph{heat-kernel grounded} \tN]
$S_{\mathrm{rel},\chi}$ is finite, differentiable, with a local Seeley--DeWitt expansion
$\operatorname{Tr}f(D^2/\chi^2)\sim f_4\chi^4 a_0+f_2\chi^2 a_2+f_0 a_4+\cdots$. For the Lichnerowicz
Dirac operator $D^2=\nabla^2+\tfrac R4$ (so $E=-\tfrac R4$, spinor trace $\operatorname{tr}\mathbf1=4$) the
Gilkey coefficients give, per $(4\pi)^{-2}$,
\[
  a_2=\tfrac16\operatorname{tr}(6E+R\,\mathbf1)=-\tfrac R3
  \quad(\text{Einstein--Hilbert }\textstyle\int\!R),\qquad
  a_4\big|_{R^2}=\tfrac1{360}\operatorname{tr}(180E^2{+}60RE{+}5R^2\mathbf1)=\tfrac{R^2}{72}
\]
(the $R^2$/Starobinsky term), so the spectral action \emph{structurally} produces
$S_{\mathrm{eff}}=\int\!\sqrt g\,\tfrac{\Mpl^2}{2}(R+\tfrac{R^2}{6M^2})+\cdots$ with the scalaron mass ratio
fixed by the cutoff moment, $M^2/\Mpl^2=6(4\pi)^2/f_0$. The TFPT closure $M^2/\Mpl^2=\cthree^7$ fixes
$f_0=6(4\pi)^2/\cthree^7$, i.e.\ $M=\cthree^{7/2}\Mpl=3.06\times10^{13}\,$GeV --- the boundary normalisation
$\cthree$ \emph{is} the gravitational scale --- and hence the Starobinsky slow-roll forms
$n_s\simeq1-\tfrac2N$, $r\simeq\tfrac{12}{N^2}$. The $R+R^2$ \emph{structure} is convention-independent
(standard Gilkey); the precise rational $\tfrac1{72}$ and factor $6$ are the standard Dirac conventions used
here (\veri{v36\_spectral\_action\_g2.py}, \veri{v28\_gravity\_fR.py}).
\end{lemma}

\begin{winbox}[The simpler resolution: ``full QG'' for physics is the gap-decoupled admissible sector \tF]
The infinite-dimensional ambient measure (G6) is the summit, but the admissible IR sector does not wait for
it. The metric coupling is gap-dominated (G5): $2\|V_{\mathrm{metric}}\|=0.785<\Delta=6\log\tfrac32=2.433$,
so the admissible sector keeps a \emph{strictly positive} effective gap $\Delta_{\mathrm{eff}}=1.648>0$
under the stated RP and metric-coupling assumptions. A positive gap dynamically \emph{isolates} the
admissible sector from the un-built ambient/deep-UV: under those assumptions the admissible (IR) measure is
closed, and the ambient completion is decoupled from it (we do \emph{not} assert it is physically
irrelevant --- that would itself be a physical interpretation). So the honest reading is
\[
  \boxed{\ \begin{gathered}
  \text{admissible IR sector}=\text{closed under stated RP};\\[2pt]
  \text{ambient metric measure (G6)}=G_{\mathrm{metric}}\ \text{gate}
  \end{gathered}\ }
\]
G2 supplies the local action ($R+R^2$, heat-kernel); G5 supplies the decoupling of the admissible sector;
together they reduce $(G_{\mathrm{metric}})$ to the ambient projective limit (G6). \textbf{Precise status
(Alessandro's boundary):} the admissible IR sector is closed under the stated RP and gap-dominance
assumptions; the ambient metric projective measure remains a \emph{strict TOE completion target}. Its
absence does \emph{not} affect the bounded IR claim, but it \emph{does block certification as a strict
physical TOE} --- so we do not call it ``mere mathematical completeness''. \veri{v36\_spectral\_action\_g2.py}
\end{winbox}

\begin{lemma}[G3--G4 --- reflection positivity, fixed and integrated]
For each $\Theta$-invariant $g$ in the Calderón ball the physical boundary kernel
$\mathcal K_g=P_{\mathrm{adm}}\Pi_{\mathrm{phys}}\mathcal N_g^{TT}\Pi_{\mathrm{phys}}P_{\mathrm{adm}}$ is
reflection positive, $\langle\Theta F,F\rangle_{\mathcal K_g}\ge0$ (G3); and $d\mu_{\mathrm{Cal},\chi}$ is
$\Theta$-invariant, supported where G3 holds uniformly, so
$\int\langle\Theta F,F\rangle_{\mathcal K_g}\,d\mu_{\mathrm{Cal},\chi}\ge0$ (G4). \textbf{G4 is the decisive
step:} RP after integrating over dynamical metrics, not merely at fixed background.
\end{lemma}

\begin{lemma}[G5 --- gap dominance \tF]
$2\|V_{\mathrm{metric}}\|_{\mathrm{rel}}<\Delta=6\log\tfrac32$, with
$\|V_{\mathrm{metric}}\|_{\mathrm{rel}}\le248\cthree^2=\tfrac{31}{8\pi^2}=0.39262$, hence
$2\|V\|=0.7852<2.4328$ and $\Delta_{\mathrm{eff}}\ge\Delta-2\|V\|>1.647>0$. The numerical inequality is
trivial (\veri{v29\_research\_contract\_certs.py}); the work is the operator-norm bound (hard).
\end{lemma}

\begin{theorem}[Decoupling theorem --- physical low-energy claims do \emph{not} need the full $G_{\mathrm{metric}}$]
\emph{If} the admissible sector is reflection-positive (G4) and the metric coupling is gap-dominated,
$2\|V_{\mathrm{metric}}\|<\Delta=6\log\tfrac32$ (G5), \emph{then} the admissible IR measure is stable under
the ambient completion: a strictly positive effective gap $\Delta_{\mathrm{eff}}=\Delta-2\|V\|>0$ protects the
admissible sector from the (un-built) ambient/deep-UV, so every \emph{physical low-energy} read-out (masses,
mixings, $\alpha^{-1}$, the $R{+}R^2$ regime) is independent of the open ambient measure. Symbolically
\[
  \boxed{\ \mathrm{RP}\ +\ 2\|V\|<\Delta\ \Longrightarrow\ \text{admissible IR measure stable under ambient completion}\ .}
\]
Thus $(G_{\mathrm{metric}})$ is \emph{not} a diffuse ``full quantum gravity missing'' block: it is the sharply
delimited \emph{ambient projective limit} (G6), a strict-TOE certification target whose closure the
falsifiable IR physics does not depend on. \textbf{Typing:} the inequality is machine-checked \tF; the
operator-norm bound on $\|V_{\mathrm{metric}}\|$ is the conditional input.
\end{theorem}

\begin{lemma}[G6--G7 --- projective limit \& Ward identities]
A projective system $\mu_{\chi_n}$ with $\pi_{m,n*}\mu_{\chi_m}=\mu_{\chi_n}$, uniform moment bounds
$\sup_n\!\int\|g\|_{H^s}^p\,d\mu_{\chi_n}<\infty$, tightness and regulator-independence yields
$\mu_{\mathrm{QG}}=\lim\mu_\chi$ on $\mathcal G/\mathrm{Diff}$ (G6, the hardest step); the limit obeys the
BRST Ward identities $\langle s\mathcal O\rangle=0$, whence $\nabla^\mu T_{\mu\nu}=0$ and the $\eta$
boundary phase cancels the APS anomalies (G7).
\end{lemma}

\begin{keybox}[Theorem G --- the closure statement \tA\ (target)]
The relative spectral boundary kernel over the diffeomorphism-quotiented metric sector admits a
regulator-independent, reflection-positive projective-limit measure $\mu_{\mathrm{QG}}$. Its Ward
identities imply covariant conservation, and its low-curvature expansion is the TFPT $R+R^2$ seam action
\[
  f_R R_{\mu\nu}-\tfrac12 f(R)g_{\mu\nu}+(g_{\mu\nu}\Box-\nabla_\mu\nabla_\nu)f_R
  =\Mpl^{-2}T_{\mu\nu}+O(R^3/M^4),
\]
so the closed covariant equation becomes the controlled IR shadow of the full measure. \emph{Status: open;
the deepest item. G5 certified; the regime equation closed \veri{v28\_gravity\_fR.py}.}
\end{keybox}

% =====================================================================
\section*{Certifiability and recommended order}
\addcontentsline{toc}{section}{Certifiability and order}
% =====================================================================
\begin{center}\footnotesize
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\linewidth}{@{}Ylc@{}}
\toprule
\textbf{Building block} & \textbf{Machine} & \textbf{Hardness} \\
\midrule
$W_{\mathrm{wall}}$ enumeration ($C_U^{(1)}$) & Lean / Python / Wolfram & easy (\emph{done}) \\
$D_4$ fixed-locus polynomial ($C_U^{(2)}$) & Sage / Mathematica & medium \\
selector uniqueness ($C_U^{(3)}$) & interval arithmetic & medium \\
SNF, determinants, spectra & Lean & easy--medium \\
principal-symbol ellipticity (G1) & xAct / Cadabra / Lean & medium \\
gap inequality (G5) & Lean & easy (\emph{done}) \\
operator-norm bound (G5) & analysis $+$ numerics & hard \\
projective limit (G6) & not primarily machine & very hard \\
Ward identities (G7) & BV/BRST formal $+$ checks & hard \\
\bottomrule
\end{tabularx}
\end{center}

\begin{winbox}[Recommended order]
\[
  \boxed{\ (U_{\mathrm{wall}})\ \rightarrow\ \text{freeze the frontier status}\ \rightarrow\ (G_{\mathrm{metric}})\ }
\]
$(U_{\mathrm{wall}})$ can visibly upgrade the theory --- it hits the last concrete flavor ambiguity,
including the ``$11$'' --- and it is finite and falsifiable (the U2 kill switch can destroy it cheaply).
$(G_{\mathrm{metric}})$ is more fundamental but a \emph{programme}, not a single proof: heavy machinery,
with the projective limit (G6) the genuine summit.
\end{winbox}

\end{document}
