% ---------------------------------------------------------------------
%  tfpt_docset.tex -- THE canonical TFPT document-set box.
%  Single source of truth for the document list; \input by the
%  introduction and the papers. Uses only universally available
%  macros (keybox + plain LaTeX math) so it compiles in every doc.
%  Each document adds its own "You are reading document #N." line
%  directly after the \input.
% ---------------------------------------------------------------------
\begin{keybox}[The TFPT document set --- what is treated where]
\textbf{Plain language:} TFPT (Topological Fixed-Point Theory) is a small discrete compiler. Two
inputs --- the seam constant $c_3=\tfrac1{8\pi}$ and the carrier rank $g_{\mathrm{car}}=5$ --- build
$D_5\oplus A_3+\mu_4\Rightarrow E_8$ and read off the Standard Model, the constants and the scale
grammar. The development is \textbf{eight documents}, best read in order:
\begin{enumerate}[leftmargin=1.7em,itemsep=1pt]
\item \texttt{introduction} --- reading guide, compiler closure, predictions, the dependency DAG and
      the single proof ledger (\texttt{verification/status\_ledger.csv}).
\item \texttt{tfpt\_1\_architecture\_e8} --- the two axioms, the derivation map, the EM fixed point
      $\alpha^{-1}$, the $D_5\oplus A_3+\mu_4\Rightarrow E_8$ construction, the QBL theorem chain.
\item \texttt{tfpt\_2\_standard\_model} --- the SM in one $\varphi_0$-ladder formula, flavor from
      parabolic transport (sheet diamond, dual anchor, $Q_+$ cohomology), the worked closures, and
      gravity/QG as the seam response.
\item \texttt{tfpt\_3\_e8\_audit\_bootstrap} --- the seven $E_8$ slices as an audit raster, the
      cascade bridge, the M\"obius bootstrap.
\item \texttt{tfpt\_4\_frontier} --- honest status of $\eta_B$, $m_p/m_e$, Koide, dark matter,
      full QG.
\item[R.] \texttt{tfpt\_research\_contracts} --- the open gates as numbered contracts: lemma chains,
      closing theorems and machine-certifiability for $(U_{\mathrm{wall}})$ and
      $G_{\mathrm{metric}}/G_{\mathrm{net}}$, with the current reduction state.
\item[H.] \texttt{tfpt\_horizon\_readouts} --- Appendix~H (unit-system reframe, \emph{not} new
      physics): one seam constant as the universal horizon thermal code, the Nariai/anchor surface,
      the resummed seam clock.
\item[O.] \texttt{origin\_theory} --- Origin Theory: why no free fundamental number remains; the
      exact core plus one honestly-typed cyclic interpretation.
\end{enumerate}
\end{keybox}
