\documentclass[11pt]{article}
% Compile with LuaLaTeX or XeLaTeX for full Unicode support.
\usepackage{fontspec}
\setmainfont{Latin Modern Roman}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{fvextra}
\DefineVerbatimEnvironment{MyVerbatim}{Verbatim}{breaklines=true,breakanywhere=true,fontsize=\small}

\title{Geometric Self Consistency on the Orientable Double Cover}
\author{}
\date{}

\begin{document}
\maketitle
\noindent\textbf{Source PDF:} ImprovedCubic.pdf

\bigskip
\noindent\textbf{Note:} This \LaTeX\ file contains a best effort text extraction of the PDF.
Line breaks and pagination markers are preserved in a verbatim block.

\bigskip
\begin{MyVerbatim}
===== Page 1 of 2 =====
Geometric Self Consistency on the Orientable Double Cover
Independent Note
September 18, 2025
1 Geometric self consistency on the orientable double cover
1.1 Starting point and notation
We use the invariants
1 1 3 41
c = , ϕ = , δ = = 48c4, b = .
3 8π tree 6π top 256π4 3 1 10
The cubic fixed point equation (CFE) is written in the normal form
b 1
α3 Aα2 Ac2κ(ϕ ) = 0, A = 2c3, κ(ϕ ) = 1 ln , (1)
− − 3 0 3 0 2π ϕ
0
󰀓 󰀔
with the baseline geometric fixpoint ϕold = ϕ +δ .
0 tree top
1.2 Backreaction on the double cover: derivation
The same electromagnetic energy that produces the logarithm in κ(ϕ ) couples back to the
0
geometry that defines ϕ . On the orientable double cover M there are two identical boundary
0
contributions. Consider the stationary total action S [α,ϕ] = S [ϕ]+U [α,ϕ], where we
tot geom EM
retain the ϕ dependent parts, 󰁩
2
S [ϕ] = 6πϕ = 12πϕ, U [α,ϕ] = const ακ(ϕ),
geom EM
·
s=1
󰁛
with κ as in (1). Stationarity requires ∂ S = 0 and ∂ S = 0. The first condition reproduces
α tot ϕ tot
(1). Variation with respect to ϕ gives
∂S ∂κ ∂κ b 1
tot 1
0 = = 12π + const α , = . (2)
∂ϕ · ∂ϕ ∂ϕ 2π ϕ
Linearisingaroundthebaselinevalueϕold = ϕ +δ andwritingϕ = ϕold+∆ϕ,theresponse
0 tree top 0 0
∆ϕ is proportional to α. By symmetry and additivity on the two sheets the topological addend
is reduced by αδ on each sheet. Hence
top
ϕnew(α) = ϕ +δ (1 2α) (3)
0 tree top −
with no new free number. The factor two is fixed by the double cover.
Remark. Equation (3) is the minimal allowed correction built from the same ingredients that
define the CFE. It is the linear first order response in α. Higher geometric corrections with
unambiguous normalisation only shift the numerical effect slightly.
1

===== Page 2 of 2 =====
1.3 Implicit solution of the CFE with ϕ (α)
0
Insert (3) into (1) and solve implicitly for α. Numerically we obtain
α o−ld 1 = 137.036501464885822..., α n−e 1 w = 137.035990390121546...,
which lowers the deviation to CODATA 2022 from +3.665372 parts per million to 0.064121
−
parts per million. The associated geometric shift is ∆ϕ = 2αδ 1.7558 10 6, about
0 top −
− ≈ − ×
thirty three parts per million relative on ϕ .
0
The sensitivity from the implicit derivative of the cubic,
dα
=
Ac2
3 2
b
π
1
ϕ
1
0 ,
dϕ − 3α2 2Aα
0
−
evaluated at the baseline, reproduces the observed shift to better than a few parts in ten to the
eight.
1.4 Physical background
1. Same cause, same effect. Thefieldenergythatdrivesthelogarithminκ(ϕ )couplesto
0
the same geometry that sets ϕ . Self consistency therefore requires a response ∆ϕ α.
0 0
∝
2. Double cover enforces a factor two. On M the two boundary sheets contribute
equally. The electromagnetic response adds up, which yields the factor two in (3).
󰁩
3. Parsimony. Neither c nor ϕ is altered, and δ remains a fixed topological invariant.
3 tree top
Only its effective strength is slightly reduced by field energy on the two sheets.
4. Side effects are tiny. Cosmic birefringence β = ϕ /(4π) changes by about eight micro
th 0
degrees, well below present uncertainties.
1.5 Old versus new
Aspect Old: ϕ = ϕ +δ New: ϕ = ϕ +δ (1 2α)
0 tree top 0 tree top
−
Extra number no no
Geometric structure constant double cover acts
Form of κ κ(ϕ ) κ(ϕ (α))
0 0
Solution type direct implicit fixed point
α 1 137.0365014649 137.0359903901
−
Deviation to CODATA 2022 +3.665372 ppm 0.064121 ppm
−
Physical plausibility missing backreaction closed self consistency
Impact on other tests unchanged only micro degree in birefringence
1.6 Conclusion
The form ϕ (α) = ϕ +δ (1 2α) closes the only open loop in the normal form. It is math-
0 tree top
−
ematically minimal, physically required by the same energy that sources κ, and fully justified
by the orientable double cover. The resulting improvement in the prediction is already below
one tenth of one part per million.
2

\end{MyVerbatim}
\end{document}
