\documentclass[11pt,a4paper]{article}
\input{tfpt45-common}

\title{\color{tfptblue}\textbf{Electromagnetic Fixed Point and Flavor Transport}\\[0.35em]
{\Large on the Rigid TFPT Branch}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Paper 3 of the TFPT 4.5 series -- \today}}

\begin{document}
\maketitle

\begin{abstract}
This paper isolates the precision-readout layer of TFPT after the primitive kernel and carrier
packet have been fixed. It treats the electromagnetic fixed point, the transport pole of the cusp
cubic, the retained seed decoder, and the flavor transport grammar yielding $\alpha$,
$\delta_{\mathrm{ph}}$, $\lambda_C$, $\beta_{\mathrm{rad}}$, $\Omega_b$, $\theta_{13}$, CKM, and
PMNS readouts.
\end{abstract}

\begin{tfptfrontbox}
\textbf{Inputs from previous papers.} Paper 1 supplies the primitive kernel and $[u_\Sigma]=1$.
Paper 2 supplies the rigid carrier, family count, admissible occupancy, compact Higgs index, and
abelian index coefficient.

\textbf{New theorem contribution.} The electromagnetic fixed point, the transport pole, the
retained seed decoder, and the UFE-form bridge to the determinant-line response:
\[
\alpha^{-1}(0)=137.035999216\ldots,\qquad
P'(z)=0\Rightarrow\delta_{\mathrm{ph}},\qquad
\lambda_C=\sqrt{\phiz(1-\phiz)},\qquad
\beta=\beta_{\mathrm{rad}}\frac{180^\circ}{\pi}\approx 0.2424^\circ,
\]
and the structured local dyonic projection $\beta_{\mathrm{BH}}(r)\sim 16\cthree^4
Q_e^{\mathrm{eff}}Q_m^{\mathrm{eff}}/r^2$ underlying the EHT-class achromatic residual intercept
test.

\textbf{Not claimed here.} No full QFT closure, no gravity/metrology proof, no CMB, no E8, and no
large pole-mass table.

\textbf{Falsification or audit surface.} The paper fails if any numerical constant enters after the
fact, if $\alpha$ is used to tune later readouts, or if alternative discrete worlds are not visibly
ruled out by the same branch constraints.
\end{tfptfrontbox}


\begin{tfptclaimcontract}
\textbf{Claim.} Exact electromagnetic fixed point and flavor/PMNS/CKM readouts on the rigid branch.\par
\textbf{Inputs.} Papers 1--2: primitive kernel, carrier packet, family count, Higgs index, abelian index.\par
\textbf{First assumptions.} Exact seam opening $\phiseam(\alpha)$, transport pole, retained seed as UV shadow, branch budget $41$.\par
\textbf{Proof status.} Bridge/readout layer with no-knobs audit.\par
\textbf{Kill condition.} Frozen inputs move after comparison, alternative discrete worlds survive, or precision rows fail stated tests.\par
\end{tfptclaimcontract}

\tableofcontents

\section{Electromagnetic Closure}

The electromagnetic calculation is presented only after the carrier branch is fixed. The fixed
point is read as a closed-branch output:
\[
\alpha^{-1}(0)=137.035999216\ldots.
\]
The paper should include the carrier form of the electromagnetic closure and the compact audit of
which structural quantities enter the fixed point.

\section{Transport Pole}

The transport phase is governed by the cubic
\[
P(z)=(z-1)\left(z-\frac{64}{729}\right)\left(z-\frac{1}{729}\right),
\qquad
P'(z)=0.
\]
The lower critical point determines $\delta_{\mathrm{ph}}$ on the retained branch. The transport
pole must be introduced as a branch consequence, not as a fit parameter.

\section{Retained Seed Decoder}

The retained seed
\[
u:=\phiz
\]
projects to the bridge observables
\[
\lambda_C=\sqrt{\phiz(1-\phiz)},
\qquad
\beta_{\mathrm{rad}}=\frac{\phiz}{4\pi},
\qquad
\sin^2\theta_{13}=\phiz e^{-\gamma}.
\]
The text should make explicit which earlier theorem fixes each symbol before it appears in a
readout.

\subsection{Compact UFE bridge for the birefringence seed}
\label{ssec:ufe-birefringence-bridge}

Before the determinant-line response is invoked in its full form, the same retained seed admits a
short bridge derivation that connects the boundary-normalised axion--photon coupling to the
cosmological birefringence amplitude. Starting from the unified-field-equation reduction of the
seam transfer, the dimensionless axion--photon anomaly coefficient is
\[
g_{a\gamma\gamma}=-4\,\cthree=-\frac{1}{2\pi},
\]
and the modified Maxwell sector responds to a constant axion increment $\Delta a=\phiz$ on the
admissible branch. The local rotation rate per unit determinant-line phase is then
\[
\beta = 2\,\cthree\,\Delta a,
\]
so substituting $\Delta a=\phiz$ and $\cthree=\tfrac{1}{8\pi}$ recovers the seed identity
\begin{equation}
\label{eq:beta-rad-ufe-bridge}
\beta_{\mathrm{rad}}=\frac{\phiz}{4\pi},
\qquad
\beta=\beta_{\mathrm{rad}}\!\times\!\frac{180^\circ}{\pi}\;\approx\;0.2424^\circ.
\end{equation}
This compact reduction is intended as a reader bridge; the determinant-line / Chern--Simons
formulation of Paper~3 and Paper~4 remains the load-bearing derivation.

\begin{remark}[Achromatic, dyonic intercept and the $\alpha$-kernel]
\label{rem:dyonic-intercept-alpha-kernel}
The same admissibility data emits a structured \emph{local} astrophysical $\beta$ amplitude in
the magnetised inflow region of a compact object,
\begin{equation}
\label{eq:beta-bh-paper3}
\beta_{\mathrm{BH}}(r)\;\sim\;\frac{Q_e^{\mathrm{eff}}\,Q_m^{\mathrm{eff}}}{256\pi^4\,r^2}
\;=\;16\,\cthree^4\,\frac{Q_e^{\mathrm{eff}}\,Q_m^{\mathrm{eff}}}{r^2}
\;=\;\frac{\deltatop}{3}\,\frac{Q_e^{\mathrm{eff}}\,Q_m^{\mathrm{eff}}}{r^2},
\end{equation}
where $\deltatop=48\cthree^4$ is the same topological coefficient that controls the precision-zone
correction of the $\alpha$-kernel. The corresponding observation channel is the achromatic
\emph{residual intercept} of the linear-polarization angle in horizon-scale polarimetry,
\[
\chi_0^{\mathrm{res}}(x)
=
\chi_0^{\mathrm{obs}}(x)-\chi_0^{\mathrm{GRMHD}}(x),
\]
i.e.\ the part of $\chi_0$ left after the GRMHD/synchrotron forward model and calibration are
subtracted. The TFPT contribution is the structured component of $\chi_0^{\mathrm{res}}(x)$ with
the spatial $1/r^2$ profile of \eqref{eq:beta-bh-paper3} and a sign flip under reversal of the
effective $E\!\cdot\!B$ orientation. The coupling $1/(256\pi^4)$ is fixed; the geometric weights
$Q_e^{\mathrm{eff}}(x), Q_m^{\mathrm{eff}}(x)$ and the emission radius are model dependent. A
dedicated standalone prediction note states the full observation protocol and three independent
null tests (frequency, spatial profile, sign flip).
\end{remark}

\section{Flavor Transport}

The CKM and PMNS closure block belongs here, together with the transport grammar and regularized
Yukawa kernels needed for the flavor statements. Representative hard readouts include
\[
|V_{ub}|=\frac{|V_{us}|^3}{3}.
\]
Large mass tables belong in the companion or a later empirical ledger, not in this paper.

\section{No-Knobs Audit}

\begin{center}
\begin{tabularx}{\textwidth}{@{}p{0.18\textwidth}p{0.2\textwidth}p{0.18\textwidth}p{0.13\textwidth}Y@{}}
\toprule
\textbf{Constant} & \textbf{First appearance} & \textbf{Prior dependency} & \textbf{Before $\alpha$?} & \textbf{Variation consequence} \\
\midrule
$Y$ & Paper 2 carrier theorem & Paper 1 primitive kernel & Yes & Breaks $3+2$, gauge quotient, and all downstream readouts. \\
$[u_\Sigma]$ & Paper 1 seam generator & Boundary primitive kernel & Yes & Breaks family counting and transport branch normalization. \\
$\phiz$ & Transport branch & Papers 1--2 & Yes & Moves $\lambda_C$, $\beta_{\mathrm{rad}}$, $\theta_{13}$, and flavor transport together. \\
$N_\Phi$ & Paper 2 Higgs index & Carrier/Higgs discharge & Yes & Changes the electromagnetic budget. \\
$\bone$ & Paper 2 abelian index & Carrier packet & Yes & Changes the fixed-point coefficient. \\
\bottomrule
\end{tabularx}
\end{center}

\section{Alternative Discrete Worlds}

The alternative discrete worlds table is a falsification device. It should not be presented as
decorative numerics. Each alternative must fail because it breaks a prior branch constraint, the
fixed-point equation, or the simultaneous reuse audit.

\clearpage
\section{Main Technical Development}

This section contains the main technical development assigned to this paper by the TFPT 4.5 clean split. Cross-paper background is referenced through dependency and scope boxes; extended backend material is kept in the Technical Companion.

\input{source_extracts/03_em_flavor_source.tex}

\section{Source Extraction Map}

\begin{tfptsourcebox}
Use \sourceDraft:
\begin{itemize}[leftmargin=1.5em]
    \item Sections 4.1 and 4.2 for electromagnetic closure.
    \item Sections 5.4 and 5.5 for UV seed shadow, Cabibbo inversion, and alternative discrete
    worlds.
    \item Sections 7.1--7.3 for the discrete phase operator, transport grammar, and Yukawa kernels.
    \item Sections 7.16--7.27 for CKM and PMNS closure.
    \item Appendix A only as a narrow operational prediction surface and compact prediction ledger.
    \item Add a dedicated $\alpha$ audit appendix inside this paper.
\end{itemize}
\end{tfptsourcebox}

\begin{tfptwarningbox}
Do not import full QFT closure, gravity, CMB, E8, or large mass tables. This is the precision
prediction paper, and its credibility depends on a short no-knobs audit.
\end{tfptwarningbox}


\begin{tfptexports}
Exports: $\alpha_\star$, $\delta_{\mathrm{ph}}$, $\lambda_C$, CKM/PMNS readout rows, sectorized seed shadows, the UFE bridge for $\beta_{\mathrm{rad}}$, the achromatic dyonic intercept $\beta_{\mathrm{BH}}(r)$, and the no-knobs audit table.
\end{tfptexports}

\section{Not Used Here}

Strong-CP admissibility closure, OS/CAR reconstruction, local Minkowski nets, scattering,
gravity/metrology proofs, CMB spectra, sky realization, E8 grammar, horizons, and large pole-mass
tables are not used as proof inputs in this paper.

\clearpage
\input{source_extracts/bibliography_precision.tex}

\end{document}
