\documentclass[11pt,a4paper]{article}
\input{tfpt45-common}

\title{\color{tfptblue}\textbf{Cosmology Interfaces of the TFPT Closed Branch}\\[0.35em]
{\Large Seam Transfer, Axion Sector, Reheating, and CMB Targets}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Paper 6 of the TFPT 4.5 series -- \today}}

\begin{document}
\maketitle

\begin{abstract}
This paper isolates the downstream cosmology interface of TFPT. Cosmology is not used as a
primitive selector of the theory. It is read from the closed branch through seam transfer,
determinant-line phase, scalaron sector, axion interface, reheating input, leptogenesis input,
neutrino sector, CMB spectra, and conjectural sky-map realization targets.
\end{abstract}

\begin{tfptfrontbox}
\textbf{Inputs from previous papers.} Papers 1--5 supply the closed branch $\Tstar$, the carrier
packet, the precision branch, the admissible QFT sector, and the boundary-normalized metrology.

\textbf{New theorem contribution.} Downstream cosmology interfaces:
\[
\Lambda_{\mathrm{IR}}
=
\Mplunred^4\left[-\log\det_{\mathrm{adm}}(1-U_\Sigma)\right],
\qquad
S_\Sigma=\log\mu_\Sigma(\alpha_\star),
\qquad
N_{\mathrm{DW}}=1,
\]
with axion, reheating, leptogenesis, and CMB targets stated at their proper status levels.

\textbf{Not claimed here.} No carrier proofs, no full $\alpha$ derivation, no QFT closure proof,
and no Standard-Model packet proof.

\textbf{Falsification or audit surface.} The paper fails if CMB Stage 2 is sold as a theorem, if a
good CMB world is conflated with this observed sky realization, or if cosmology is allowed to tune
the primitive branch.
\end{tfptfrontbox}

\begin{tfptwarningbox}
CMB and E8 must never be written as hard theorem claims in this paper. Stage 1 is spectra. Stage 2
is sky realization as a conjectural or programmatic target.
\end{tfptwarningbox}


\begin{tfptclaimcontract}
\textbf{Claim.} Closed branch exports cosmology interface data: seam transfer, axion interface, reheating/leptogenesis inputs, and CMB Stage 1/2 targets.\par
\textbf{Inputs.} Fixed $\Tstar$, metrology layer, determinant-line phase, scalaron and neutrino sectors.\par
\textbf{First assumptions.} Infrared continuation and nonequilibrium solver are separate comparison-layer inputs.\par
\textbf{Proof status.} Downstream interface; Stage 2 sky realization is programmatic/conjectural.\par
\textbf{Kill condition.} Cosmology tunes the primitive branch or Stage 2 is presented as theorem-level sky reconstruction.\par
\end{tfptclaimcontract}

\tableofcontents

\section{Cosmology as Downstream Interface}

The closed branch is fixed before cosmology enters:
\[
\Tstar
\Rightarrow
(U_\Sigma,\det_{\mathrm{adm}},\text{scalaron branch},\text{neutrino sector})
\Rightarrow
\text{cosmology interfaces}.
\]
This section should make the nonprimitive status of cosmology explicit.

\section{Seam Transfer and Infrared Determinant}

The seam-transfer expression is
\[
\Lambda_{\mathrm{IR}}
=
\Mplunred^4\left[-\log\det_{\mathrm{adm}}(1-U_\Sigma)\right].
\]
The text should state which part is theorem-level interface data and which part is an empirical
comparison convention.

\section{Axion Interface}

The axion sector is recorded as
\[
S_\Sigma=\log\mu_\Sigma(\alpha_\star),
\qquad
N_{\mathrm{DW}}=1,
\qquad
\theta_i=\pi(1-\phiseam(\alpha_\star)).
\]
The axion interface belongs here because it depends on seam transfer and determinant-line phase,
not on the primitive carrier proof.

\section{Reheating, Leptogenesis, and Neutrino Inputs}

Reheating and leptogenesis are stated as downstream inputs supplied by the closed branch. The paper
should keep them status-coded and avoid turning the module into a hidden fit engine for later CMB
targets.

\section{CMB Stage 1: Spectra}

Stage 1 is the spectral target: transfer functions, angular spectra, and comparison rows. This
stage may define falsification targets and benchmark rows, but it does not claim a unique sky-map
realization.

\section{CMB Stage 2: Sky Realization}

Stage 2 is a conjectural realization target. The source draft's distinction should remain explicit:
a good CMB world is not automatically this CMB world. The map-realization layer therefore belongs
in a programmatic or conditional section, not in the theorem stack.

\section{Downstream Obligations Moved to the Companion}

\begin{center}
\begin{tabularx}{\textwidth}{@{}p{0.28\textwidth}Y@{}}
\toprule
\textbf{Module} & \textbf{Status in this paper} \\
\midrule
Stationary horizons and compact objects & Listed only as downstream programmatic obligations; technical material is in the Companion. \\
Code subspace, pointer dynamics, and record algebra & Not part of the cosmology-interface proof surface. \\
Transient event channels & Falsification and prediction semantics belong to the Companion. \\
Pole masses, Higgs readout, and full flavor output & Inputs from earlier readout papers or Companion ledgers, not cosmology claims. \\
Extended comparison ledgers & Companion-only material. \\
\bottomrule
\end{tabularx}
\end{center}

\clearpage
\section{Main Technical Development}

This section contains the main technical development assigned to this paper by the TFPT 4.5 clean split. Cross-paper background is referenced through dependency and scope boxes; extended backend material is kept in the Technical Companion.

\input{source_extracts/06_cosmology_source.tex}

\section{Source Extraction Map}

\begin{tfptsourcebox}
Use \sourceDraft:
\begin{itemize}[leftmargin=1.5em]
    \item Section 10 for FRW reduction, seam transfer, and scalaron branch.
    \item Sections 10.1 and 10.2 for falsification matrix and proof-obligation ledger.
    \item Appendix C.7, Appendix G, and the cosmology-interface proof material in Appendix J.
    \item Appendix N only for the axion-interface excerpt.
    \item Keep CMB Stage 1 and Stage 2 visibly separate.
\end{itemize}
\end{tfptsourcebox}


\begin{tfptexports}
Exports: $\Lambda_{\mathrm{IR}}$ interface, $S_\Sigma$, $N_{\mathrm{DW}}=1$, $\theta_i$, reheating/leptogenesis input block, CMB Stage 1/2 status separation, and axion target interface.
\end{tfptexports}

\section{Not Used Here}

Carrier proofs, the full $\alpha$ derivation, QFT closure proofs, Standard-Model packet proofs,
and metrology proofs are not reproved or used as adjustable inputs in this paper. They enter only
as fixed outputs of the earlier closed branch.

\clearpage
\input{source_extracts/bibliography_cosmology.tex}

\end{document}
