\documentclass[11pt,a4paper]{article}
\input{tfpt45-common}

\title{\color{tfptblue}\textbf{TFPT 4.5 Paper Series Index}\\[0.35em]
{\Large Split by Burden of Proof}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Working index generated from \sourceDraft{} -- \today}}

\begin{document}
\maketitle

\begin{abstract}
This index records the dedicated TFPT 4.5 paper split. The organizing principle is not topical
coverage but review burden: each document groups claims that need the same type of scrutiny and
keeps speculative or downstream risks from contaminating the primitive core.
\end{abstract}

\tableofcontents

\section{Documents}

\begin{center}
\begin{tabularx}{\textwidth}{@{}p{0.12\textwidth}p{0.34\textwidth}Y@{}}
\toprule
\textbf{File} & \textbf{Title} & \textbf{Role} \\
\midrule
\texttt{00\_orientation\_note.tex} & TFPT in One Map & Thin entry document and dependency map. \\
\texttt{01\_boundary\_kernel.tex} & Boundary Polarization and the Primitive Kernel of TFPT & Primitive boundary kernel. \\
\texttt{02\_carrier\_rigidity\_standard\_model\_packet.tex} & Carrier Rigidity, Hypercharge, and the Standard Model Packet & Carrier theorem and SM packet. \\
\texttt{03\_electromagnetic\_closure\_flavor\_transport.tex} & Electromagnetic Fixed Point and Flavor Transport & Precision prediction and no-knobs audit. \\
\texttt{04\_admissibility\_strong\_cp\_qft\_closure.tex} & Admissibility, Strong CP, and Nonperturbative QFT Closure & Conditional QFT closure layer. \\
\texttt{05\_geometric\_hodge\_closure\_dimensionless\_metrology.tex} & Geometric Hodge Closure and Dimensionless Metrology & Boundary-normalized metrology. \\
\texttt{06\_cosmology\_interfaces\_downstream\_closure.tex} & Cosmology Interfaces of the TFPT Closed Branch & Downstream cosmology interfaces and CMB targets. \\
\texttt{technical\_companion.tex} & Technical Companion to TFPT & Long toolbox, conventions, ledgers, continuations. \\
\texttt{tfpt45\_theory\_map.tex} & TFPT -- Von Boundary Struktur zu beobachtbarer Realit\"at & Vector status map of the staged derivation chain. \\
\bottomrule
\end{tabularx}
\end{center}

\section{Mathematical Dependency Order}

\begin{enumerate}[leftmargin=1.5em]
    \item Paper 1: boundary primitive kernel.
    \item Paper 2: carrier rigidity and Standard-Model packet.
    \item Paper 3: electromagnetic and flavor readouts.
    \item Paper 4: admissibility, strong CP, positivity, OS/local-net/scattering closure.
    \item Paper 5: geometric branch and dimensionless metrology.
    \item Paper 6: downstream cosmology interfaces.
\end{enumerate}

\section{Recommended Public Order}

\begin{enumerate}[leftmargin=1.5em]
    \item Paper 0 as public orientation.
    \item Paper 2 as first visible core result.
    \item Paper 1 as formal foundation backbone.
    \item Paper 3 as prediction paper.
    \item Papers 4 and 5 as analytic and metrological stabilization.
    \item Paper 6 as downstream expansion.
\end{enumerate}

\section{Per-Paper Front-Box Rule}

Every paper begins with the same four-part box:
\begin{enumerate}[leftmargin=1.5em]
    \item Inputs from previous papers.
    \item New theorem contribution.
    \item Not claimed here.
    \item Falsification or audit surface.
\end{enumerate}
This is a deliberate anti-evasion device: each document states how it can fail. Each paper also
ends with a short ``Not used here'' list so that excluded material does not re-enter through a
back-door support appendix.

\section{Global Exclusion Discipline}

\begin{center}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}Y@{}}
\toprule
\textbf{Paper} & \textbf{Explicit exclusions} \\
\midrule
Paper 1 & Carrier, SM group, $\alpha$, flavor, gravity, cosmology, E8. \\
Paper 2 & Exact $\alpha$, CKM, PMNS, masses, OS reconstruction, cosmology, E8. \\
Paper 3 & Full QFT closure, gravity, CMB, E8, large mass tables. \\
Paper 4 & $\alpha$ detail calculation, CMB, E8, full empirical tables. \\
Paper 5 & Late-time $H_0$, CMB, black holes, horizons, E8 stage atlas, astrophysical bursts. \\
Paper 6 & Carrier proofs, full $\alpha$ derivation, QFT closure proofs, SM packet proof. \\
\bottomrule
\end{tabularx}
\end{center}

\section{Source}

All documents in this folder are based on \sourceDraft. The dedicated papers are intentionally
clean splits: they keep their own primary source body and refer cross-paper material through
dependency boxes. The Technical Companion is the designated home for full appendix-level ballast,
extended ledgers, optional continuations, E8 grammar, horizons, record algebra, and transient
channels.

\end{document}
