\documentclass[11pt,a4paper]{article}
\input{tfpt45-common}

\title{\color{tfptblue}\textbf{Technical Companion to TFPT}\\[0.35em]
{\Large Conventions, Positivity, APS Interfaces, and Comparison Maps}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Companion document for the TFPT 4.5 paper series -- \today}}

\begin{document}
\maketitle

\begin{abstract}
The Technical Companion is the long toolbox for the TFPT paper series. It holds conventions,
analytic interfaces, auxiliary proofs, extended comparison maps, empirical ledgers, optional
continuations, record algebra, horizon material, transient channels, and the E8 stage atlas. It is
not a stand-alone theorem paper and should not be required reading for the primitive kernel or the
carrier theorem.
\end{abstract}

\begin{tfptfrontbox}
\textbf{Inputs from previous papers.} The entire TFPT 4.5 paper series.

\textbf{New theorem contribution.} None by default. Companion material can support theorem papers,
but new claims should be promoted into the appropriate paper rather than hidden here.

\textbf{Not claimed here.} The companion does not replace Papers 1--6 and does not elevate
comparison maps or optional continuations to theorem status.

\textbf{Falsification or audit surface.} The companion fails if it blurs theorem, standard-theorem
interface, empirical comparison, optional continuation, and programmatic target language.
\end{tfptfrontbox}

\tableofcontents

\section{Purpose}

The companion exists to keep the six papers short enough to be reviewed by the right audiences. A
reader checking the carrier theorem should not be forced to read CMB sky maps, E8 scale grammar,
record algebra, or horizon continuations.

\section{Core Convention Blocks}

The first part collects:
\begin{itemize}[leftmargin=1.5em]
    \item symbol guide,
    \item relative objects,
    \item layered datum and admissibility conventions,
    \item APS and superconnection setup,
    \item positivity conventions,
    \item theorem-status vocabulary.
\end{itemize}

\section{Analytic Backend}

This part holds expanded details for:
\begin{itemize}[leftmargin=1.5em]
    \item relative reflection positivity with fermions,
    \item admissible OS reconstruction,
    \item asymptotic scattering,
    \item dressed massless interface,
    \item exact admissible flow and 1PI expansion details,
    \item Yukawa kernels and positivity lemmas.
\end{itemize}

\section{Comparison Backend}

This part holds:
\begin{itemize}[leftmargin=1.5em]
    \item constants atlas,
    \item extended benchmarks,
    \item compact and full empirical ledgers,
    \item residual readout and interface refinements,
    \item operational prediction matrix,
    \item target and kill-test rows,
    \item novelty boundary and literature positioning.
\end{itemize}

\section{Downstream and Optional Continuations}

This part holds material that should not drive the primitive theorem chain:
\begin{itemize}[leftmargin=1.5em]
    \item E8 stage atlas,
    \item optional arithmetic continuations,
    \item infrared seam-transfer continuations,
    \item horizon continuations,
    \item record algebra and pointer dynamics,
    \item information-theoretic readings,
    \item cut-and-project readings,
    \item transient event channels.
\end{itemize}

\clearpage
\section{Main Technical Development}

This section contains the main technical development assigned to this paper by the TFPT 4.5 clean split. Cross-paper background is referenced through dependency and scope boxes; extended backend material is kept in the Technical Companion.

\input{source_extracts/technical_companion_source.tex}

\section{Source Extraction Map}

\begin{tfptsourcebox}
Use \sourceDraft:
\begin{itemize}[leftmargin=1.5em]
    \item Appendix-level empirical readout sections.
    \item Technical conventions and data layers.
    \item Constants atlas and downstream scale grammar.
    \item Relative APS and superconnection setup.
    \item Relative reflection positivity with fermions.
    \item Admissible OS reconstruction and asymptotic scattering.
    \item FRW reduction and cosmology interface proofs.
    \item Yukawa kernels and positivity lemmas.
    \item Information-theoretic and cut-and-project readings.
    \item Record algebra and pointer dynamics.
    \item Horizons, modular flow, and black hole thermality.
    \item Prediction semantics and transient event channels.
    \item Closed theoretical outputs and empirical comparison surface.
    \item Extended benchmarks and novelty boundary.
\end{itemize}
\end{tfptsourcebox}

\section{Promotion Rule}

If a companion item becomes load-bearing for a theorem paper, it must be promoted into that paper's
technical backend or cited as a named standard-theorem interface. The companion should never be the
place where a major assumption first becomes invisible.

\end{document}
