\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Neutrino Reactor Angle from the Closed PMNS Branch}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the TFPT row for the reactor angle. The formula retains the compact seed expression, while the status assignment is the neutrino closure map.
\end{abstract}

\PredictionStatus{$\sin^2\theta_{13}=0.02311$}{Physical observable; neutrino closure readout.}{neutrino readout $N_
u$}{robust normal-ordering global-fit exclusion at the stated confidence level.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Neutrino closure}{$\sin^2\theta_{13}$}{The UV identity is a shadow; the operational row belongs to PMNS/neutrino closure.}{NuFIT exclusion}

\section{Derivation}

The compact UV identity is
\[
\sin^2\theta_{13}=\phiz e^{-\gamma},
\qquad
\phiz=\frac{1}{6\pi}+\frac{3}{256\pi^4},
\qquad
\gamma=\frac56.
\]
After sectorization, the physical row is read as
\[
\Tstar\longmapsto N_\nu(\Tstar)\longmapsto |(U_{\mathrm{PMNS}}^\star)_{e3}|^2.
\]
The benchmark target recorded in the prediction table is
\[
\sin^2\theta_{13}=0.02311.
\]
The comparison convention used in the ledger is the NuFIT normal-ordering representative.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The row must not be presented as a free seed projection. Its operational status is neutrino closure; the seed expression is only a compact UV shadow.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
