\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Baryon Asymmetry from the Leptogenesis Interface}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the baryon-asymmetry row as a downstream leptogenesis comparison target.
\end{abstract}

\PredictionStatus{$\eta_B=5.97\times10^{-10}$}{Cosmology comparison; flavored leptogenesis interface.}{cosmology comparison $C_{\mathrm{cos}}$}{robust exclusion of the quoted branch value under the declared Boltzmann solver.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Leptogenesis interface}{$\eta_B$}{The row is downstream of reheating and heavy-neutrino input data.}{asymmetry mismatch}

\section{Derivation}

The cosmology interface fixes a reheating / leptogenesis input block
\[
(\Lambda_{\mathrm{IR}},N_{\mathrm{DW}},\theta_i,T_R,\mathcal I_{\mathrm{LG}}).
\]
The flavored Boltzmann system has schematic form
\[
\frac{dY_{N_i}}{dz}=-D_i(Y_{N_i}-Y_{N_i}^{eq}),
\qquad
\frac{dY_{\Delta_\alpha}}{dz}=\sum_i\epsilon_{i\alpha}D_i(Y_{N_i}-Y_{N_i}^{eq})-W_{i\alpha}Y_{\Delta_\alpha}.
\]
The operational target recorded in the ledger is
\[
\eta_B=5.97\times10^{-10}.
\]


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The numerical asymmetry is a comparison-layer solution of the declared nonequilibrium system; it is not a primitive constant.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
