\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Strong-CP Closure and the Neutron-EDM Null Test}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the strong-CP prediction as a theorem-level null row. It is a consequence of determinant-line closure and admissibility, not a tunable flavor-sector phase.
\end{abstract}

\PredictionStatus{$\theta_{\mathrm{eff}}=0$}{Theorem-level null prediction on the admissible branch.}{strong-CP closure $C_{\mathrm{CP}}$}{stable nonzero hadronic EDM signal.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Admissibility and determinant-line closure}{$\theta_{\mathrm{eff}}=0$}{Strong CP belongs to admissibility/QFT closure, not to the flavor paper.}{nonzero EDM}

\section{Derivation}

On the admissible branch the determinant-line closure gives
\[
\arg\det M_u=\arg\det M_d=0.
\]
Together with the admissible topological-sector positivity and sheet symmetry, the effective strong angle is
\[
\theta_{\mathrm{eff}}=0.
\]
The physical null row is therefore
\[
\bar\theta=0,
\qquad
F(\theta)>F(0)\quad\text{for}\quad \theta\not\equiv0\ \mathrm{mod}\ 2\pi.
\]
The experimental pressure point is the hadronic EDM program.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{A stable nonzero hadronic EDM signal would break the present determinant-line strong-CP closure rather than merely shift a fit parameter.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
