\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: No Second Light Seam-Even Higgs Doublet}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the no-second-light-Higgs kill test. It is a structural consequence of the compact bosonic index and carrier/Higgs closure.
\end{abstract}

\PredictionStatus{no additional seam-even light doublet}{Kill test of the bosonic-index route.}{compact Higgs index / carrier packet}{robust discovery of a second light seam-even Higgs doublet.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Bosonic index}{single light Higgs}{The compact bosonic index fixes $N_\Phi=1$.}{second light doublet}

\section{Derivation}

On the carrier branch the compact bosonic index fixes the determinant class
\[
(c_1(L_2),c_1(L_3))=(1,0),
\]
with exactly one weak doublet and no unavoidable light color triplet. Equivalently,
\[
N_\Phi=1.
\]
The prediction is therefore a prohibition:
\[
\text{no additional seam-even light Higgs doublet on the minimal branch.}
\]


\section{No-Knobs and Failure Surface}
\NoKnobsBox{A robust discovery of a second light seam-even Higgs doublet would falsify the bosonic-index route used by the present carrier/Higgs closure.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
