\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Cabibbo Angle from the Retained Flavor Branch}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the Cabibbo-angle prediction as a flavor-sector readout. The UV seed identity is retained as an exact shadow, but the physical observable is assigned to the flavor closure map.
\end{abstract}

\PredictionStatus{$\lambda_C=0.22438$}{Physical observable; flavor readout from hard holonomy closure.}{flavor readout $F_{\mathrm{fl}}$}{stable CKM global-fit mismatch after the declared comparison map.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Flavor transport}{$\lambda_C$}{The retained seed appears only as UV bookkeeping; the physical row factors through flavor closure.}{CKM mismatch}

\section{Derivation}

On the retained UV bookkeeping layer the seed obeys
\[
\lambda_C=\sqrt{\phiz(1-\phiz)},
\qquad
\phiz=\frac{1}{6\pi}+\frac{3}{256\pi^4}.
\]
Equivalently, the Cabibbo inversion is
\[
\phiz=\frac{1-\sqrt{1-4\lambda_C^2}}{2}.
\]
In the physical observable layer this identity is not treated as an independent seed quartet. The row factors through the flavor map
\[
\Tstar\longmapsto F_{\mathrm{fl}}(\Tstar)\longmapsto s_{12}(V_{\mathrm{CKM}}^\star)=\lambda_C.
\]
The numerical target used in the prediction ledger is
\[
\lambda_C=0.22438,
\]
compared to the CKM physical angle representative.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{Do not count $\lambda_C$, $\beta_{\mathrm{rad}}$, $\Omega_b$, and $\theta_{13}$ as one operational class. $\lambda_C$ is the flavor member of the sectorized seed shadow.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
