\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Exact Electromagnetic Closure and the Fine-Structure Constant}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the TFPT prediction for the Thomson-limit fine-structure constant. The row is not a fit: it is the positive root of the carrier-form electromagnetic closure equation with the exact seam generating function.
\end{abstract}

\PredictionStatus{$\alpha^{-1}(0)=137.0359992168407\ldots$}{Physical observable; exact electromagnetic closure on the minimal seam mode.}{electromagnetic closure $C_{\mathrm{em}}$}{failure of the self-consistent root equation or a stable precision mismatch outside the stated interface uncertainty.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Electromagnetic closure}{$\alpha^{-1}(0)$}{Carrier budget and exact seam opening enter before the root is evaluated.}{root or residual failure}

\section{Derivation}

The electromagnetic row uses the exact seam opening, not the frozen retained seed. With
\[
\cthree=\frac{1}{8\pi},\qquad b_1=\frac{41}{10},\qquad
\sum_{f,j}L_{f,j}^{\mathrm{diag}}+N_\Phi=41,
\]
define
\[
\phiseam(\alpha)=\frac{1}{6\pi}+\frac{3e^{-2\alpha}}{256\pi^4}
\left(1-\frac{3e^{-2\alpha}}{256\pi^4}\right)^{-5/4}.
\]
The closure function is
\[
F_{U(1)}(\alpha)=\alpha^3-2\cthree^3\alpha^2-
\frac45\cthree^6\left(\sum_{f,j}L_{f,j}^{\mathrm{diag}}+N_\Phi\right)
\log\bigl(\phiseam(\alpha)^{-1}\bigr).
\]
The prediction is the unique positive root
\[
F_{U(1)}(\alpha_\star)=0,
\qquad
\alpha_\star=0.007297352562209853\ldots,
\qquad
\alpha_\star^{-1}=137.0359992168407\ldots .
\]


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The exact opening $\phiseam(\alpha)$ must remain inside the root equation. Freezing it at $\phiz$ shifts the result by about $5.02\times10^{-4}$ in $\alpha^{-1}$ and is not the benchmark definition.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
