\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Rare-Kaon Corridor from the Closed CKM Point}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the rare-kaon corridor. It follows the closed CKM point into standard short-distance rare-kaon amplitudes and is compared against NA62/KOTO-style channels.
\end{abstract}

\PredictionStatus{$\mathrm{BR}(K^+)=9.40\times10^{-11}$, $\mathrm{BR}(K_L)=3.47\times10^{-11}$}{Comparison quantity; flavor readout through short-distance amplitudes.}{flavor readout $F_{\mathrm{fl}}$}{$K^+$ outside $[7,12]\times10^{-11}$ or incompatible Grossman--Nir-plane correlation.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Flavor comparison}{$K\to\pi\nu\bar\nu$}{Closed CKM point enters the short-distance kaon amplitudes.}{corridor failure}

\section{Derivation}

The flavor sector fixes a closed CKM point. The rare-kaon comparison row then evaluates the short-distance amplitudes at that point:
\[
\mathrm{BR}(K^+\to\pi^+\nu\bar\nu)=9.40\times10^{-11},
\]
\[
\mathrm{BR}(K_L\to\pi^0\nu\bar\nu)=3.47\times10^{-11}.
\]
The current charged-channel reading quoted in the ledger is compatible with the target corridor, while the neutral channel remains open.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{This row is not a theorem-level Standard-Model proof; it is a flavor-comparison target. A stable $K^+$ value outside $[7,12]\times10^{-11}$ or a GN-plane mismatch would break the present flavor bridge.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
