\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Axion Haloscope Window from the Seam-Transfer Cosmology Interface}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the axion haloscope window as a downstream cosmology readout target. It is not a primitive selector of the theory.
\end{abstract}

\PredictionStatus{$m_a\simeq65.19\,\mu\mathrm{eV}$, $\nu_a\simeq15.764\,\mathrm{GHz}$}{Cosmology readout target.}{cosmology readout $C_{\mathrm{cos}}$}{exclusion in $15.764\,\mathrm{GHz}\pm50\,\mathrm{MHz}$ at the coupled sensitivity.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Axion interface}{haloscope window}{The row is downstream of seam transfer and determinant-line phase.}{window exclusion}

\section{Derivation}

The determinant-line axion interface fixes
\[
N_{\mathrm{DW}}=1,
\qquad
\theta_i=\pi\bigl(1-\phiseam(\alpha_\star)\bigr),
\]
with seam-transfer and scalaron inputs supplying the cosmology interface. The closed-branch target recorded in the ledger is
\[
f_a\approx8.86\times10^{10}\,\mathrm{GeV},
\qquad
m_a\approx65.19\,\mu\mathrm{eV},
\qquad
\nu_a\approx15.764\,\mathrm{GHz}.
\]
The associated coupled sensitivity row is
\[
|g_{a\gamma\gamma}^{(\mathrm{phys})}|\approx1.80\times10^{-12}\,\mathrm{GeV}^{-1}.
\]


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The practical scan target is $15.764\,\mathrm{GHz}\pm50\,\mathrm{MHz}$. Exclusion in the relevant coupled window pressures the intrinsic axion row.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
