\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Baryon Fraction as a Cosmology Comparison Row}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the baryon-fraction row as a cosmology comparison rather than a primitive seed observable. The value is compared only after the declared late-time interface.
\end{abstract}

\PredictionStatus{$\Omega_b=0.04894$}{Cosmology comparison; present-epoch reconstruction.}{cosmology readout $C_{\mathrm{cos}}$}{robust inconsistency of the density-readout package under the declared Planck comparison convention.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Cosmology comparison}{$\Omega_b$}{The row is present-epoch comparison, not a timeless UV observable.}{density package mismatch}

\section{Derivation}

The appendix comparison convention reconstructs the present-epoch baryon fraction from the Planck pair
\[
\Omega_b=\frac{\Omega_b h^2}{h^2},
\qquad
h=\frac{H_0}{100}.
\]
TFPT assigns the row to the cosmology package
\[
\Tstar\longmapsto C_{\mathrm{cos}}(\Tstar)\longmapsto \Omega_b.
\]
The compact UV identity
\[
\Omega_b=(4\pi-1)\beta_{\mathrm{rad}}
\]
is retained only as bookkeeping. The prediction ledger target is
\[
\Omega_b=0.04894,
\]
with Planck 2018 comparison representative $0.04930$ and residual $-0.421\sigma$ in the stated snapshot.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The row is not a primitive cosmological dial and not one member of an operational seed quartet. It is a late-time comparison image of the cosmology readout map.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
