\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Intrinsic Neutrino Mass Sum on the Closed Branch}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the neutrino mass-sum row as an intrinsic normal-ordering output of the closed neutrino branch.
\end{abstract}

\PredictionStatus{$\Sigma m_\nu=5.8764\times10^{-2}\,\mathrm{eV}$}{Physical observable / comparison quantity; neutrino closure readout.}{neutrino readout $N_
u$}{robust cosmological upper bound below the branch value.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Neutrino closure}{$\Sigma m_\nu$}{No external oscillation inversion is used as primitive input.}{bound below target}

\section{Derivation}

The intrinsic neutrino closure row gives
\[
m_{\nu_1}=0,
\qquad
m_{\nu_2}=8.614\times10^{-3}\,\mathrm{eV},
\qquad
m_{\nu_3}=5.015\times10^{-2}\,\mathrm{eV}.
\]
Thus
\[
\Sigma m_\nu=m_{\nu_1}+m_{\nu_2}+m_{\nu_3}
=5.8764\times10^{-2}\,\mathrm{eV}.
\]
The row is compared to cosmological mass-sum analyses only after the neutrino closure map has fixed the internal value.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{A robust upper bound below the branch value would pressure the closed neutrino sector, not merely a comparison convention.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
