\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Cosmic Birefringence from Determinant-Line Response}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the cosmic-birefringence row as a determinant-line response. It is not part of a single seed quartet in the physical observable layer.
\end{abstract}

\PredictionStatus{$\beta=0.2424^\circ$}{Physical observable; determinant-line/Chern--Simons response.}{determinant response $R_{\mathrm{CS}}$}{externally calibrated $\beta=0$ within $\pm0.05^\circ$.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Determinant response}{$\beta$}{The response row is sectorized away from the old seed quartet.}{calibrated null}

\section{Derivation}

The retained UV expression is
\[
\beta_{\mathrm{rad}}=\frac{\phiz}{4\pi},
\qquad
\phiz=\frac{1}{6\pi}+\frac{3}{256\pi^4}.
\]
In degrees this gives the row recorded as
\[
\beta=0.2424^\circ.
\]
The physical dependency class is not the old seed quartet but the determinant-line response
\[
\Tstar\longmapsto R_{\mathrm{CS}}(\Tstar)\longmapsto \beta.
\]
The comparison row is made against calibrated CMB rotation analyses without EB self-nulling.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The direct falsifier is a calibrated achromatic CMB rotation analysis consistent with $\beta=0$ inside $\pm0.05^\circ$ under the declared convention.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
