\input{../tfpt45-common}

\newcommand{\PredictionStatus}[4]{%
\begin{tcolorbox}[colback=tfptblue!2, colframe=tfptblue!45, breakable,
    title={Prediction scope and audit}, colbacktitle=tfptblue!65]
\textbf{Target.} #1

\textbf{Status.} #2

\textbf{Dependency class.} #3

\textbf{Kill or pressure test.} #4
\end{tcolorbox}}

\newcommand{\MinimalKernelBox}{%
\begin{tcolorbox}[colback=tfptgreen!3, colframe=tfptgreen!50, breakable,
    title={Minimal TFPT kernel used in this prediction}, colbacktitle=tfptgreen!65]
The standalone input package is the boundary-polarized closed branch
\[
\mathfrak S_{\min}\Rightarrow\mathcal B_{\min}\Rightarrow\Tbound
\Rightarrow(\taudbl,\iC,\Pprim,[u_\Sigma],\cthree)
\Rightarrow d^\star_{\mathrm{disc}}\Rightarrow \Padm\Rightarrow\Tstar.
\]
The prediction uses only the sector map named in its audit box. Numerical comparison conventions
are not theorem inputs; they enter only at the final interface row.
\end{tcolorbox}}

\newcommand{\DependencyDiagram}[4]{%
\begin{center}
\begin{tikzpicture}[
    node distance=11mm,
    box/.style={rectangle, rounded corners=2pt, draw=tfptblue!65, fill=tfptblue!5,
        align=center, text width=3.1cm, inner sep=5pt, font=\small\sffamily},
    predout/.style={rectangle, rounded corners=2pt, draw=tfptorange!70!black, fill=tfptorange!8,
        align=center, text width=3.4cm, inner sep=5pt, font=\small\sffamily},
    arr/.style={-{Latex[length=2.3mm]}, thick, draw=tfptgray!85}
]
\node[box] (kernel) {Boundary primitive\\kernel};
\node[box, right=of kernel] (branch) {Rigid closed\\branch $\Tstar$};
\node[box, right=of branch] (sector) {#1};
\node[predout, right=of sector] (target) {#2};
\draw[arr] (kernel) -- (branch);
\draw[arr] (branch) -- (sector);
\draw[arr] (sector) -- (target);
\node[below=6mm of branch, text width=9.5cm, align=center, font=\footnotesize\sffamily\color{tfptgray}]
{#3};
\node[below=4mm of target, text width=3.4cm, align=center, font=\footnotesize\sffamily\color{tfptorange!70!black}]
{#4};
\end{tikzpicture}
\end{center}}

\newcommand{\NoKnobsBox}[1]{%
\begin{tcolorbox}[colback=tfptorange!4, colframe=tfptorange!55, breakable,
    title={No-knobs audit}, colbacktitle=tfptorange!75]
#1
\end{tcolorbox}}

\newcommand{\PredictionBibliography}{%
\begin{thebibliography}{99}
\bibitem{aps1975}
M.~F.~Atiyah, V.~K.~Patodi, and I.~M.~Singer,
\newblock \emph{Spectral asymmetry and Riemannian geometry. I},
\newblock Math. Proc. Cambridge Philos. Soc. \textbf{77} (1975), 43--69.

\bibitem{chamseddineConnes1997}
A.~H.~Chamseddine and A.~Connes,
\newblock \emph{The spectral action principle},
\newblock Commun. Math. Phys. \textbf{186} (1997), 731--750.

\bibitem{codata2022}
P.~J.~Mohr, D.~B.~Newell, and B.~N.~Taylor,
\newblock \emph{CODATA recommended values of the fundamental physical constants: 2022 update},
\newblock NIST / CODATA reference set, accessed March 2026.

\bibitem{pdg2025}
S.~Navas et al.\ (Particle Data Group),
\newblock \emph{Review of Particle Physics},
\newblock Phys.\ Rev.\ D \textbf{110} (2024), 030001; 2025 online update.

\bibitem{nufit2025}
NuFIT Collaboration,
\newblock \emph{NuFIT global analysis of neutrino oscillation data},
\newblock website snapshot based on data available through November 2025.

\bibitem{planck2018}
Planck Collaboration,
\newblock \emph{Planck 2018 results. VI. Cosmological parameters},
\newblock Astron. Astrophys. \textbf{641} (2020), A6.

\bibitem{minamiKomatsu2020}
Y.~Minami and E.~Komatsu,
\newblock \emph{New extraction of the cosmic birefringence from the Planck 2018 polarization data},
\newblock Phys. Rev. Lett. \textbf{125} (2020), 221301.

\bibitem{na62Moriond2026}
X.~Chang et al.\ (for the NA62 Collaboration),
\newblock \emph{New measurement of $K^{+}\to\pi^{+}\nu\bar{\nu}$ branching ratio at the NA62 experiment},
\newblock arXiv:2604.12649.

\bibitem{koto2024}
KOTO Collaboration,
\newblock \emph{Search for the $K_{L}\to\pi^{0}\nu\bar{\nu}$ decay at the J-PARC KOTO experiment},
\newblock arXiv:2411.11237.
\end{thebibliography}}
