\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Running Electromagnetic Scheme Projection at the Z Pole}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the Z-pole electromagnetic scheme projection. It is not the primary electromagnetic theorem row; it is a declared projection of the closed alpha(0) output.
\end{abstract}

\PredictionStatus{$\bar\alpha^{(5)}(M_Z)^{-1}=127.9405$}{Scheme projection; not a primitive observable.}{threshold/scheme projection $T_{\mathrm{phys}}$}{persistent mismatch after declared Standard-Model threshold map.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Scheme projection}{$\bar\alpha^{(5)}(M_Z)^{-1}$}{This row projects the exact alpha(0) readout through a declared scheme map.}{scheme mismatch}

\section{Derivation}

The physical electromagnetic input is the exact closure value
\[
\alpha^{-1}(0)=137.0359992168\ldots.
\]
The Z-pole comparison row is obtained only after the declared scheme map
\[
\mathcal R_{\SM}[\alpha(0)]
\]
is applied. The representative in the ledger is
\[
\bar\alpha^{(5)}(M_Z)^{-1}=127.9405.
\]
Its status is therefore scheme projection, not a separate primitive prediction.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{The row must not be used as an independent fitting input. It is downstream of alpha(0) and the declared threshold convention.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
