\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Neutral-Pion Hadronic Check from the Closed Branch}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the neutral-pion row as a derived hadronic check of the closed branch.
\end{abstract}

\PredictionStatus{$m_{\pi^0}=134.979\,\mathrm{MeV}$}{Derived hadronic row / out-of-sample check.}{hadronic closure}{robust mismatch outside the stated uncertainty budget.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Hadronic readout}{$m_{\pi^0}$}{The row is derived from the hadronic branch, not used to fix it.}{hadronic mismatch}

\section{Derivation}

The supplementary ledger records the neutral-pion row as a GMOR relation from the light-quark combination,
\[
m_{\pi^0}\quad\text{from}\quad (m_u+m_d)\ \text{and}\ \langle\bar q q\rangle.
\]
The comparison representative is
\[
m_{\pi^0}=134.979\,\mathrm{MeV}.
\]
This row is not used to tune the carrier or flavor branch; it is an out-of-sample hadronic consistency check.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{A robust mismatch outside the stated hadronic uncertainty budget would pressure the hadronic readout, not the primitive boundary kernel directly.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
