\documentclass[11pt,a4paper]{article}
\input{tfpt_prediction_common}
\title{\color{tfptblue}\textbf{TFPT Prediction: Majorana Neutrinoless-Double-Beta Row}}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{{\normalsize\color{tfptgray}\sffamily Standalone prediction note -- \today}}
\begin{document}
\maketitle

\begin{abstract}
This note isolates the neutrinoless-double-beta row as a Majorana-branch comparison target.
\end{abstract}

\PredictionStatus{$m_{\beta\beta}=1.516\times10^{-3}\,\mathrm{eV}$}{Comparison quantity; Majorana lattice on the closed neutrino branch.}{neutrino readout $N_
u$}{light-Majorana detection implying $m_{\beta\beta}\gtrsim10^{-2}\,\mathrm{eV}$.}


\section{Standalone Minimal Kernel}
\MinimalKernelBox

The paper is intentionally one-row: it does not reprove the full TFPT series. It states the minimal closed-branch input needed for this prediction, shows the sector map, and gives the direct failure mode. The source status follows the TFPT 4.5 split: boundary and carrier inputs are core, electromagnetic/flavor/metrology inputs are bridge readouts, QFT closure is conditional, and cosmology rows are downstream comparison targets when explicitly marked.


\section{Dependency Graph}
\DependencyDiagram{Majorana neutrino closure}{$m_{\beta\beta}$}{The row is a low-amplitude Majorana target, not a high-mass inverted-ordering signal.}{large signal}

\section{Derivation}

On the closed Majorana neutrino branch the effective mass row is recorded as
\[
m_{\beta\beta}=1.516\times10^{-3}\,\mathrm{eV}.
\]
It is generated by the same neutrino closure package that fixes the PMNS matrix and the intrinsic normal-ordering mass sum. The row is therefore a low-amplitude light-Majorana target.


\section{No-Knobs and Failure Surface}
\NoKnobsBox{A detection that robustly implies $m_{\beta\beta}\gtrsim10^{-2}\,\mathrm{eV}$ would be incompatible with the present closed Majorana branch.}

\section{Minimal Submission Claim}
The standalone claim is limited to the displayed target and dependency class. It does not assert
that every comparison row of the full TFPT ledger has the same proof status. Any update of the
upstream boundary kernel, carrier theorem, or sector map must be propagated into this prediction
before the numerical row is distributed.

\PredictionBibliography

\end{document}
